---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bibliomatrix

<!-- badges: start -->
<!-- badges: end -->

The goal of bibliomatrix is to provide a common set of functionality for the Annual Bibliometric Monitoring efforts from the Bibliometrics team at the KTH Library.

## Installation

You can install the latest development version of bibliomatrix from [GitHub](https://KTH-Library.github.com/bibliomatrix) with:

``` r
# install.packages("devtools")
devtools::install_github("KTH-Library/bibliomatrix")
```

## Example

This is a basic example which shows you how to get some data when creating Annual Bibliometric Monitoring analytics:

```{r example, message=FALSE}
library(bibliomatrix)
library(dplyr)

# simple example showing how to filter some of the data for Table 1
# in the ABM report for an organizational unit and restrict the
# output to a specific set of columns

abm_tab1() %>% 
filter(unit_long == "KTH Royal Institute of Technology") %>%
select(unit_long, `Publication Type`, `WoS Coverage`) %>%
knitr::kable()

```

```{r}

```

