---
title: ABM - Topics
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    favicon: KTH_logo_RGB_svart.png
    fig_mobile: FALSE
params:
  citation_topic: 1

---

```{css echo=FALSE}
@font-face {
  font-family: 'Figtree Light';
  font-style: normal;
  font-weight: 400;
  src: url('fonts/figtree-v5-latin_latin-ext-regular.woff2') format('woff2');
}

body {
  font-family: 'Figtree Light';
}
@font-face {
  font-family: 'Figtree';
  font-style: normal;
  font-weight: 400;
  src: url('fonts/figtree-v5-latin_latin-ext-regular.woff2') format('woff2');
}


```


```{r setup, include=FALSE}
# unit_codes for testing:
# 
# u1g9umtq
# u1jr9fll 
# u1ygqmuy
# u13bp6vd
# u18qe64m
# u1o2ujjd

library(flexdashboard)
library(DT)
library(readr)
library(purrr)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(bibliomatrix)
library(tidyr)
library(scales)
library(kableExtra)
library(glue)
library(extrafont)
library(kthapi)
library(DBI)
library(ktheme)
#library(tidyquant)
library(zoo)
library(plotly)

colors_vb <- palette_kth_neo(17)

# Retrieve result tables to use in tabs and key indicators

con <- con_bib("mssql")

aid <- abm_config()$analysis_id
topic <- params$citation_topic

dataquery <- sprintf(
  "SELECT m.*, t.Content_id, t.Content_type, t.Citation_topic
   FROM masterfile m
   INNER JOIN BIBMET.dbo.Document d ON (d.UT = m.WebofScience_Id)
   INNER JOIN BIBMET.dbo.Citation_topic t ON (t.UID = d.UID)
   WHERE m.analysis_id = %s
     AND t.Content_id = '%s'
     AND m.level = 0",
  aid,
  topic)

data <- dbGetQuery(con, dataquery)

topic_name <- data |> head(1) |> pull(Citation_topic)
unit_label <- topic_name
unit_file_label <- unit_label

firstyear <- as.integer(abm_config()$start_year)
lastyear <- as.integer(abm_config()$stop_year)

df_diva <- abm_table1(data, analysis_start = firstyear, analysis_stop = lastyear)
df_diva_full <- abm_table1_full(data, analysis_start = firstyear, analysis_stop = lastyear)
df_cit3y <- abm_table2(data, analysis_start = firstyear, analysis_stop = lastyear)
df_cf <- abm_table3(data, analysis_start = firstyear, analysis_stop = lastyear)
df_jcf <- abm_table4(data, analysis_start = firstyear, analysis_stop = lastyear)
df_copub <- abm_table5(data, analysis_start = firstyear, analysis_stop = lastyear)
df_oa <- abm_table6(data, analysis_start = firstyear, analysis_stop = lastyear)
df_scop_cit <- abm_table_scop_cit(data, analysis_start = firstyear, analysis_stop = lastyear)
df_scop_normcit <- abm_table_scop_normcit(data, analysis_start = firstyear, analysis_stop = lastyear)
df_scop_snip <- abm_table_scop_snip(data, analysis_start = firstyear, analysis_stop = lastyear)
df_scop_copub <- abm_table_scop_copub(data, analysis_start = firstyear, analysis_stop = lastyear)

analysis_date <- get_analysis_date(con = con)

df_sdg_year <- abm_sdg_year(con = con,
                            data = data,
                            analysisId = abm_config()$analysis_id,
                            analysis_start = abm_config()$start_year,
                            analysis_stop = abm_config()$stop_year)
df_sdg_table <- abm_sdg_table(con = con,
                              data = data,
                              analysisId = abm_config()$analysis_id,
                              analysis_start = abm_config()$start_year,
                              analysis_stop = abm_config()$stop_year)
dbDisconnect(con)

current_date <- format(Sys.Date(), "%Y%m%d")

abm_unit_title <- paste0("ABM: ", unit_label)

STATIC <- "https://kth-library.github.io/abm"

```

<style>
<!-- TODO: this does not work in responsive mobile mode -->
.navbar-header {
  width: 0px;
  visibility: hidden;
}
.nav-tabs-custom > .nav-tabs > li > a {
  font-size: 1.5rem
}
.navbar {
  background-color:#004791;
}
</style>

<style>
#plotlydiv {
  padding: 25px;
}
</style>

Overview
===========================

#### `r unit_label`

Row {data-height=240}
---------------------

```{r}
  yrfields <- grep("^[1-2][0-9]{3}$", names(df_diva), value = TRUE)
  firstyear <- min(yrfields)
  lastyear <- max(yrfields)
  
  as_range <- function(x, delim = "-") {
    y <- as.integer(x)
    paste(collapse = delim, na.omit(dplyr::case_when(
      is.finite(y) ~ y
    )))
  }
```

### **Publications in DiVA `r as_range(lastyear)`<br>(fractional counts)**

```{r, fig.width = 1.75, fig.height = 2}
abm_ui_valuebox_publications(df_diva, lastyear, colors_vb[1], unit_label)
```

```{r}
has_rows <- df_cf %>% filter(!is.na(pubs_frac)) %>% nrow() > 0
last_interval <- ifelse(has_rows, paste((as.numeric(nth(df_cf$Publication_Year, -2))-2),nth(df_cf$Publication_Year, -2), sep = "-"), "")
```

### **[Citation impact `r last_interval` (WoS)](#citation-impact)** {.no-padding .no-mobile}

```{r, fig.width = 3.7, fig.height = 2}
abm_ui_bullet_citations(df_cf)
```

### **[Citation impact `r last_interval` (WoS)](#citation-impact)** {.no-padding .mobile}

```{r, fig.width=3.75, fig.height = 2}
abm_ui_bullet_citations(df_cf)
```

```{r}

has_rows <- df_jcf %>% filter(!is.na(pubs_frac)) %>% nrow() > 0
last_interval <- ifelse(has_rows, paste((as.numeric(nth(df_jcf$Publication_Year, -2))-2),nth(df_jcf$Publication_Year, -2), sep = "-"), "")
```
### **[Journal impact `r last_interval` (WoS)](#journal-impact)**  {.no-padding .no-mobile}

```{r, fig.width=3.8, fig.height = 2} 
abm_ui_bullet_journal(df_jcf)
```

### **[Journal impact `r last_interval` (WoS)](#journal-impact)**  {.no-padding .mobile}

```{r, fig.width=3.75, fig.height = 2}
abm_ui_bullet_journal(df_jcf)
```


```{r}
has_rows <- df_copub %>% filter(!is.na(P_full)) %>% nrow > 0
last_interval <- ifelse(has_rows, paste((as.numeric(nth(df_copub$Publication_Year, -2))-2),nth(df_copub$Publication_Year, -2), sep = "-"), "")
```

### **[Co&#8209;publishing `r last_interval` (WoS)](#copublishing)** {.no-padding .no-mobile}
```{r, fig.width=3.75, fig.height = 2}
abm_ui_waffle_copub(df_copub)
```

### **[Co&#8209;publishing `r last_interval` (WoS)](#copublishing)** {.no-padding .mobile}

```{r, fig.width=2.75, fig.height = 2}
abm_ui_waffle_copub(df_copub)
```

Row {data-height=500}
--------------------------------

### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.html#overview){target="_blank" style="position:relative;float:right;"}

The selection of publications in this report is based on Web of Science citation topics. Therefore only publications that can be matched to Web of Science, excluding Emerging Sources, are included. The publication years covered are `r abm_config()$start_year` to `r abm_config()$stop_year`. Indicators in the Citation impact, Journal impact and Co&#8209;publishing tabs are based on Web of Science publications only. Corresponding Scopus indicators can be found under the Scopus tab.

Only publications which have been affiliated to KTH are included. This means that publications written by a researcher before she/he was employed at KTH, and that are not affiliated to KTH, will not be included in the statistics.

Extraction of publications and indicators from the KTH bibliometric database BibMet was conducted at `r analysis_date`.

### **Publication volume** {.no-padding .no-mobile } 

<!-- <div id="plotlydiv"> .no-padding  -->

```{r, fig.width=8}
if (nrow(df_diva) > 0) {
  p <- (abm_graph_diva(df_diva) +
    theme(axis.title.x = element_blank())) |>
    abm_plotlyfy(tooltip = c("text")) |>  # c("y", "x", "fill")
    style(hovertemplate = paste0("<b>%{data.legendgroup}</b><br>",
                                 "<b>Publication year: </b> %{x}<br>",
                                 "<b>Publication volume, frac: </b>%{text}<br><extra></extra>")) |>
    layout(
      font = list(family = "Figtree"),
      autosize = TRUE,
      showlegend = TRUE,
      margin = list(l = 30, t = 40, r = 30),
      legend = list(
        y            = -0.2,
        xanchor      = "middle",
        orientation  = "h"
      ))
  
  p
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```

### **Publication volume** {.no-padding .mobile}

```{r, fig.width=8, fig.height = 5}
if (nrow(df_diva) > 0) {
  p
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
``` 

Publication summary
=====================================

#### `r unit_label`


Row 
---------------------

### **Publication volume** {.no-padding .no-mobile}

```{r, fig.width=10, fig.height=5}
if (nrow(df_diva) > 0) {
  p <- (abm_graph_diva(df_diva) +
    theme(axis.title.x = element_blank())) |> 
    abm_plotlyfy(tooltip = c("text")) |>  # c("y","fill", "x")
    #layout(margin = list(l = 30, t = 40, r = 30)) |> # trying some extra spacing 
    style(hovertemplate = paste0("<b>%{data.legendgroup}</b><br>",
                                 "<b>Publication year:</b> %{x}<br>",
                                 "<b>Publication volume, frac:</b> %{text}<br><extra></extra>")) |>
    layout(
      autosize = TRUE,
      showlegend = TRUE,
      margin = list(l = 30, t = 40, r = 30),
      legend = list(
        y            = -0.2,
        xanchor      = "middle",
        orientation  = "h"
      ))
  p
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```

### **Publication volume** {.no-padding .mobile}

```{r, fig.width=8, fig.height = 5}
if (nrow(df_diva) > 0) {
  p
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
``` 

Row {.tabset data-height=700}
---------------------

### Fractional count
#### **Publication volume, fractionalized** {.no-padding .no-mobile}

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>


```{r}
abm_ui_datatable_diva(
  df_diva,
  unit_file_label = unit_file_label,
  unit_title = abm_unit_title
)

```

#### **Publication volume, fractionalized** {.no-padding .mobile}

```{r, fig.width=3.75}
abm_ui_kable_diva(df_diva)
```

### Full count
#### **Publication volume, full count** {.no-padding .no-mobile}

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>

```{r}

abm_ui_datatable_diva_full(
  df_diva_full, 
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)

```

#### **Publication volume, full count** {.no-padding .mobile}

```{r, fig.width=3.75}
abm_ui_kable_diva_full(df_diva_full)
```


Citation impact
=====================================

#### `r unit_label`


Row
---------------------

### **Average field normalized citations (Cf)** <br> `r timegraph_header_legend()`

```{r, fig.width=7, fig.height=4}
if (df_cf %>% filter(!is.na(pubs_frac)) %>% nrow() > 0){
  time_graph(df_cf, indicator = "cf", ma = TRUE, weight = "pubs_frac", refline = 1, ylabel = "Average Cf") |>
    abm_plotlyfy(tooltip = c("y","x")) |> 
    style(hovertemplate = paste0("<b>Publication year:</b> %{x}<br>",
                                 "<b>Cf:</b> %{y:.3r}<extra></extra>"))
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```


### **Share of publications among Top 10% cited** <br> `r timegraph_header_legend()`

```{r, fig.width=7, fig.height=4}
if (df_cf %>% filter(!is.na(pubs_frac)) %>% nrow() > 0){
  time_graph(df_cf, indicator = "top10_share", ma = TRUE, weight = "pubs_frac", 
             refline = .1, percent = TRUE, ylabel = "Share Top 10%") |>
    abm_plotlyfy(tooltip = c("y","x")) |> 
        style(hovertemplate = paste0("<b>Publication year:</b> %{x}<br>",
                                 "<b>Share Top 10%:</b> %{y:.1%}<extra></extra>"))
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```


Row {data-height=550}
---------------------

### **Citations 3-year window, fractional counts** {.no-mobile}

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>
```{r}
abm_ui_datatable_cit3y(
  df_cit3y, 
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)
```

### **Citations 3-year window, fractional counts** {.mobile}

```{r}
abm_ui_kable_cit3y(df_cit3y)
```

### **Field normalized citations, fractionalized** {.no-mobile}

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>

```{r}
abm_ui_datatable_cf(
  df_cf,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)
```

### **Field normalized citations, fractionalized** {.no-padding .mobile}

```{r}
abm_ui_kable_cf(df_cf)
```


Row
--------------------

### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.html#citation-impact){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis"}
cat("This table is based on Web of Science publication types Article, Proceedings paper, Review, Letter and Editorial.<br>")
```

### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.html#citation-impact){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis"}
cat("This table is based on Web of Science publication types Article and Review.<br>")
```


Journal impact <!-- {data-orientation=columns} -->
=====================================

#### `r unit_label`

Row {data-width=700}
-----------------------

### **Field normalized journal impact (JCf)** <br> `r timegraph_header_legend()`

```{r, fig.dim=c(8,4), out.height='40%', out.width='90%'}
if(df_jcf %>% filter(!is.na(pubs_frac)) %>% nrow() > 0) {
  time_graph(df_jcf, indicator = "jcf", ma = TRUE, weight = "pubs_frac", refline = 1, "Average Journal Cf") |>
    abm_plotlyfy(tooltip = c("y","x")) |>
    style(hovertemplate = paste0("<b>Publication year:</b> %{x}<br>",
                                 "<b>Journal Cf:</b> %{y:.3r}<extra></extra>"))
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```


### **Share of publications in Top 20% journals** <br> `r timegraph_header_legend()`

```{r, fig.dim=c(8,4), out.height='40%', out.width='90%'}
if(df_cf %>% filter(!is.na(pubs_frac)) %>% nrow() > 0) {
  time_graph(df_jcf, indicator = "top20_share", ma = TRUE, weight = "pubs_frac", refline = .2, "Share Journal Top 20%", percent = TRUE) |>
    abm_plotlyfy(tooltip = c("y","x")) |>
    style(hovertemplate = paste0("<b>Publication year:</b> %{x}<br>",
                                 "<b>Share Top 20% journals:</b> %{y:.1%}}<extra></extra>"))
    
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```


Row  {data-width=600; data-height=550}
-----------------------

### **Journal impact, fractionalized** {.no-mobile}

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>

```{r, fig.width=6, fig.height=4, out.height='40%'}
abm_ui_datatable_jcf(
  df_jcf,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)
```

### **Journal impact, fractionalized** {.no-padding .mobile}

```{r, fig.width=3.75}
abm_ui_kable_jcf(df_jcf)
```

### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.html#journal-impact){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis"}
cat("This table is based on Web of Science publication types Article and Review.<br>")
```

Co&#8209;publishing {data-orientation=rows}
=====================================

#### `r unit_label`

Row {.tabset data-height=6000}
------------------------------

### Summary

<div style='display:flex; flex-direction:row; justify-content:space-evenly; align-items:start;'>

<div style='width: 50%; max-width: 750px;'>

#### **International and Swedish non-university co&#8209;publication**

```{r, fig.width=6, fig.height=5, out.width='95%'}
if(df_copub %>% filter(!is.na(P_full)) %>% nrow() > 0) {
  (abm_graph_copub(df_copub) + 
    theme(axis.title.x = element_blank())) |>
    abm_plotlyfy(tooltip = c("y","x")) |> 
    style(hovertemplate = paste0("<b>%{data.legendgroup}</b><br>",
                                  "<b>Publication year:</b> %{x}<br>",
                                  "<b>Share co-publication:</b> %{y:.1%}<extra></extra>")) |>
    layout(legend = list(orientation = "h",
                         yanchor = "bottom",
                         y = -0.20,
                         x = 0.5,
                         xanchor = "center"))
  
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```

</div>

<div style='width: 50%; max-width: 900px;'>

#### **International and Swedish non-university co&#8209;publications (full counts)** {.no-mobile}

```{r, fig.width=6, fig.height=4}
abm_ui_datatable_copub(
  df_copub,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)
```

#### **International and Swedish non-university co&#8209;publications (full counts)** {.no-padding .mobile}

```{r}
abm_ui_kable_copub(df_copub)
```

#### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.html#co-publishing){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis"}
cat("This table is based on Web of Science publication types Article and Review.<br>")
```

</div>
</div>

Open Access
=====================================

#### `r unit_label`

Row
---------------------

### **Open Access status by year, share** 

```{r, fig.width=8}
if (df_oa %>% filter(!is.na(P_tot)) %>% nrow() > 0) {
  abm_graph_oa_lines(df_oa) |>
    abm_plotlyfy(tooltip = c("y","x")) |> 
    layout(legend = list(orientation = "h",
                         yanchor = "bottom",
                         y = -0.35,
                         x = 0.5,
                         xanchor = "center")) |>
    style(hovertemplate = paste0("<b>%{data.legendgroup}</b><br>",
                                 "<b>Publication year:</b> %{x}<br>",
                                 "<b>Share OA:</b> %{y:.1%}<extra></extra>"))
  
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```

### **Open Access status by year, number of publications**

```{r, fig.width=8}
if (df_oa %>% filter(!is.na(P_tot)) %>% nrow() > 0) {
  abm_graph_oadata_stackedarea(df_oa) |>
    abm_plotlyfy(tooltip = c("text")) |>   # c("y","x")
    layout(legend = list(orientation = "h",
                         yanchor = "bottom",
                         y = -0.32,
                         x = 0.5,
                         xanchor = "center")) |>
    style(hovertemplate = paste0("<b>%{data.legendgroup}</b><br>",
          "<b>Publication year:</b> %{x}<br>",
          "<b>No publications:</b> %{text}<extra></extra>"))
  
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```

Row {data-height=550}
---------------------

### **Open Access publications, full counts** {.no-mobile}
<!-- The DT table headers may have a right alignment issue due to some whitespace issue artifact from disabled sorting? -->
<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
.table th {
  text-align: right;
}
</style>

```{r}
abm_ui_datatable_oa(
  df_oa,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)

```

### **Open Access publications, full counts** {.no-padding .mobile}

```{r, fig.width=3.75}
abm_ui_kable_oa(df_oa)
```

Row
-------

### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.html#open-access){target="_blank" style="position:relative;float:right;"}

The Open Access type of the publications was fetched from [OpenAlex](https://openalex.org). The method to determine the OA type is presented on  [OpenAlex support pages](https://help.openalex.org/hc/en-us/articles/24347035046295-Open-Access-OA). However, note that we count the bronze category as Not OA, since there is no identifyable license.

In summary, the different OA types can be described as follows:

- *Diamond*: The full text has been found on a publisher website, there is no article publication cost.

- *Gold:* The full text has been found on a publisher website, in a journal that is fully OA.

- *Hybrid:* The full text has been found on a publisher website, in a journal that is not fully OA.

- *Green:* The full text has been found in an institutional repository, such as DiVA.

**N.B.**: This table is based on peer-reviewed publications for which OpenAlex could determine the OA type (necessary condition: have a DOI number). OpenAlex's method is empirical and does not strictly equate to copyright license. As a consequence, the OA status of a given publication may vary with time --- for example turning from *"Not OA"* to *"Green"* when a full text is added to DiVA.


Scopus
=====================================

#### `r unit_label`

Row {.tabset data-height=1800}
------------------------------

### Citation Impact

<div style='display:flex; flex-direction:row; justify-content:space-evenly; align-items:start;'>

<div style='width: 50%; max-width: 800px;'>

#### **Average field weighted citation impact (FWCI)** <br> `r timegraph_header_legend()`

```{r, fig.height = 4, fig.width = 6, out.width='85%'}
if(df_scop_normcit %>% filter(!is.na(pubs_frac)) %>% nrow() > 0) {
  time_graph(df_scop_normcit, "fwci_x", ma = TRUE, weight = "pubs_frac", ylabel = "Average FWCI", refline = 1) |>
    abm_plotlyfy(tooltip = c("y","x")) |> 
    style(hovertemplate = paste0("<b>Publication year:</b> %{x}<br>",
                                 "<b>FWCI:</b> %{y:.3r}<extra></extra>"))
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```


#### **Citations, open window** {.no-mobile}

<style>
div.dt-buttons {
  position:relative;
  float:right;
}
</style>

```{r, fig.width = 6, out.width='85%'}
abm_ui_datatable_scop_cit(
  df_scop_cit,
  unit_file_label = unit_file_label,
  unit_title = abm_unit_title
)
```

#### **Citations, open window** {.mobile}

```{r}
abm_ui_kable_scop_cit(df_scop_cit)
```


#### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.html#scopus){target="_blank" style="position:relative;float:right;"}
```{r, echo=FALSE, results="asis", out.width='85%'}
cat("This table is based on Scopus publication types Article, Conference Paper, Review, Letter and Editorial.<br>")
```

</div>

<!-- <div style='display:flex; flex-direction:row; justify-content:space-evenly; align-items:start;'> -->

<!-- <div style='width: 45%;'> -->
<div style='width: 50%; max-width: 800px;'>

##### **Share of publications among Top 10% cited** <br> `r timegraph_header_legend()`

```{r, fig.height = 4, fig.width = 6, out.width='85%'}
if(df_scop_normcit %>% filter(!is.na(pubs_frac)) %>% nrow() > 0) {
  time_graph(df_scop_normcit, "top10_share", ma = TRUE, weight = "pubs_frac", ylabel = "Share Top 10%", refline = .1, percent = TRUE) |>
    abm_plotlyfy(tooltip = c("y","x")) |> 
    style(hovertemplate = paste0("<b>Publication year:</b> %{x}<br>",
                                 "<b>Share Top 10%:</b> %{y:.1%}<extra></extra>"))
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```

<!-- <div style='width: 45%;'> -->
<!-- <div style='width: 50%; max-width: 800px;'> -->

##### **Field weighted citation impact (FWCI)** {.no-mobile}

```{r, fig.width = 6, out.width='85%'}
abm_ui_datatable_scop_normcit(
  df_scop_normcit,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)
```

#### **Field weighted citation impact (FWCI)** {.mobile}

```{r}
abm_ui_kable_scop_normcit(df_scop_normcit)
```

#### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.html#scopus){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis", out.width='85%'}
cat("This table is based on Scopus publication types Article, Review and Conference Paper.<br>")
```

</div>
</div>

### Journal Impact

<div style='display:flex; flex-direction:row; justify-content:space-evenly; align-items:start;'>

<div style='width: 50%; max-width: 800px;'>

#### **Field normalized journal impact (SNIP)** <br> `r timegraph_header_legend()`

```{r, fig.height = 3, fig.width = 6, out.width='95%'}
if(df_scop_snip %>% filter(!is.na(pubs_frac)) %>% nrow() > 0) {
  time_graph(df_scop_snip, "avg_snip", ma = TRUE, weight = "pubs_frac", ylabel = "Average SNIP", refline = 1) |>
    abm_plotlyfy(tooltip = c("y","x")) |> 
    style(hovertemplate = paste0("<b>Publication year:</b> %{x}<br>",
                                 "<b>SNIP:</b> %{y:.3r}<extra></extra>"))
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```  

#### **Journal impact, fractionalized** {.no-mobile}

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>

```{r, fig.height=4, fig.width=6, out.width='95%'}
abm_ui_datatable_scop_snip(
  df_scop_snip,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)
```

#### **Journal impact, fractionalized** {.mobile}

```{r, out.width='95%'}
abm_ui_kable_scop_snip(df_scop_snip)
```


</div>

<div style='width: 50%; max-width: 800px;'>

#### **Share of publications in Top 20% journals** <br> `r timegraph_header_legend()`

```{r, fig.height = 3, fig.width = 6, out.width='95%'}
if(df_scop_snip %>% filter(!is.na(pubs_frac)) %>% nrow() > 0) {
  time_graph(df_scop_snip, "top20_share", ma = TRUE, weight = "pubs_frac", ylabel = "Share Top 20%", refline = .2, percent = TRUE) |>
    abm_plotlyfy(tooltip = c("y","x")) |> 
    style(hovertemplate = paste0("<b>Publication year:</b> %{x}<br>",
                                 "<b>Share Top 20% journals:</b> %{y:.1%}<extra></extra>"))
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```  


#### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.html#scopus){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis", out.width='95%'}
cat("This table is based on Scopus publication types Article, Review and Conference Paper.<br>")
```

</div>
</div>

### Co&#8209;publishing


<div style='display:flex; flex-direction:row; justify-content:space-evenly; align-items:start;'>

<div style='width: 50%; max-width: 750px;'>

#### **International and corporate co&#8209;publication**

```{r, fig.width=6, fig.height=5, out.width='95%'}
if(df_scop_copub %>% filter(!is.na(P_full)) %>% nrow() > 0) {
  (abm_graph_scop_copub(df_scop_copub) + 
    theme(axis.title.x = element_blank())) |>
    abm_plotlyfy(tooltip = c("y","x")) |>
    style(hovertemplate = paste0("<b>%{data.legendgroup}</b><br>",
                                 "<b>Publication year:</b> %{x}<br>",
                                 "<b>Share co-publication:</b> %{y:.1%}<extra></extra>")) |>
    layout(legend = list(orientation = "h",
                         yanchor = "bottom",
                         y = -0.20,
                         x = 0.5,
                         xanchor = "center"))
  
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```

</div>

<div style='width: 50%; max-width: 900px;'>

#### **International and corporate co&#8209;publications (full counts)** {.no-mobile}

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>

```{r, out.width='100%'}
abm_ui_datatable_scop_copub(
  df_scop_copub,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)
```

#### **International and corporate co&#8209;publications (full counts)** {.mobile}

```{r}
abm_ui_kable_scop_copub(df_scop_copub)
```

#### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.html#scopus){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis", out.width = '100%'}
cat("This table is based on Scopus publication types Article, Review and Conference Paper.<br>")
```

</div>
</div>

SDG
=====================================

#### `r unit_label`

Row {data-height=650}
---------------------

### **Sustainable Development Goals** {.no-mobile}

```{r, fig.height=8, fig.width = 20}
if(df_sdg_table %>% filter(SDG_Displayname != 'None') %>% nrow() > 0) {
  abm_graph_sdg(df_sdg_table) |>
    abm_plotlyfy(tooltip = c("y","x")) |>
    style(hovertemplate = paste0("<b>%{y}</b><br>",
            "<b>Publication volume, frac:</b> %{x}</b><br><extra></extra>"))
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```


### **Sustainable Development Goals** {.mobile}

```{r, fig.height=8, fig.width = 6}
if(df_sdg_table %>% filter(SDG_Displayname != 'None') %>% nrow() > 0) {
  abm_graph_sdg_mobile(df_sdg_table)
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```


Row {data-height=800}
---------------------

### **Publications with any Sustainable Development Goal** {.no-mobile}

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>

```{r, fig.height = 4}
abm_ui_datatable_sdg_year(
  df_sdg_year,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)
```

### **Publications with any Sustainable Development Goal** {.mobile}

```{r}
abm_ui_kable_sdg_year(df_sdg_year)
```


### **Sustainable Development Goals** {.no-mobile}

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>

```{r, fig.height = 4}
abm_ui_datatable_sdg_table(
  df_sdg_table,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)
```

### **Sustainable Development Goals** {.mobile}

```{r}
abm_ui_kable_sdg_table(df_sdg_table)
```

Row
---------------------

### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.html#sdg){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis"}
cat("This table is based on Scopus publication types Article, Review and Conference Paper.<br>")
```

### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.html#sdg){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis"}
cat("This table is based on Scopus publication types Article, Review and Conference Paper.<br>")
```

<i class="fa fa-info-circle" aria-hidden="true"></i> About
===========================

#### 

Row  {data-height=1024}
---------------------

<iframe allowfullscreen="true" src="https://KTH-Library.github.io/abm/About_ABM.html" style="border: 0px solid #ddd; min-height: 1024px" width="100%" height="100%" data-external="1"></iframe>
