---
title: "ABM"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    favicon: kth-logo.png
params:
  unit_code: !r bibliomatrix:::abm_config()$default_unit
  is_employee: FALSE
  use_package_data: TRUE
  embed_data: FALSE
---

```{r setup, include=FALSE}
# unit_codes for testing:

# u1g9umtq
# u1jr9fll 
# u1ygqmuy
# u13bp6vd
# u18qe64m   <- NB: this one triggers an exception in sliding_intervals() fcn

library(flexdashboard)
library(DT)
library(readr)
library(purrr)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(bibliomatrix)
library(tidyr)
library(scales)
library(glue)

colors_vb <- palette_kth(4)
run_unit <- params$unit_code


# Retrieve result tables to use in tabs and key indicators

if (params$use_package_data != TRUE) {
  con <- pool_bib()
  df_diva <- abm_table1(con = con, unit_code = run_unit) 
  df_cit3y <- abm_table2(con = con, unit_code= run_unit)
  df_cf <- abm_table3(con = con, unit_code= run_unit)
  df_jcf <- abm_table4(con = con, unit_code= run_unit)
  df_copub <- abm_table5(con = con, unit_code = run_unit)
  df_woscov <- abm_woscoverage(con = con, unit_code = run_unit)
  unit_meta <- unit_info(con = con) %>% filter(unit_code == run_unit)
  pool::poolClose(con)
} else {
  df_diva <- pluck(abm_public_kth$units, run_unit, 1)
  df_cit3y <- pluck(abm_public_kth$units, run_unit, 2)
  df_cf <- pluck(abm_public_kth$units, run_unit, 3)
  df_jcf <- pluck(abm_public_kth$units, run_unit, 4)
  df_copub <- pluck(abm_public_kth$units, run_unit, 5)
  df_woscov <- pluck(abm_public_kth$units, run_unit, "coverage")
  unit_meta <- filter(abm_public_kth$meta, unit_code == run_unit)
}

if (params$is_employee) {
  
  unit_label <- 
    ad_displayname(kthid = params$unit_code)
  
} else {
  
  unit_label <- 
    abm_public_kth$meta %>% 
    filter(unit_code == run_unit) %>%
    pull(unit_long_en)
}

```

Overview
===========================

#### `r unit_label`

Row  {data-height=240}
---------------------

```{r}
yrfields <- grep("^[1-2][0-9]{3}$", names(df_diva))
firstyear <- min(names(df_diva[yrfields]))
lastyear <- max(names(df_diva[yrfields]))
```

### **Total publications `r lastyear`<br>(fractional counts)**

```{r, fig.width = 3, fig.height = 2}
if (nrow(df_diva) > 0){
  total_pubs <- sum(df_diva[, lastyear], na.rm = TRUE)
  valueBox(
    value = round(total_pubs, 1),
    color = colors_vb[1],
    icon = "fa-chart-bar",
    href = "#publications-in-diva")
}
```

### **WoS coverage `r firstyear` - `r lastyear`<br>(peer reviewed)**

```{r, fig.width = 3, fig.height = 2}
if (nrow(df_diva) > 0){
  totcov <- df_woscov %>% filter(Publication_Type == "Peer reviewed") %>% summarise(woscov = sum(sumcov_frac) / sum(p_frac)) %>% pull(woscov)
  valueBox(
    value = paste(100*round(totcov, 3), "%"),
    color = colors_vb[1],
    icon = "fa-percent",
    href = "#publications-in-diva")
}

```

```{r}
last_interval <- ifelse(df_cf %>% filter(!is.na(P_frac)) %>% nrow() > 0,
                        nth(df_cf$interval, -2),
                        "")
```

### **[Publication indicators `r last_interval`](#citation-impact)** {.no-padding}

```{r, fig.width = 3.5, fig.height = 2}
if(df_cf %>% filter(!is.na(P_frac)) %>% nrow() > 0){
  
  cf <- as.numeric(filter(df_cf, interval == last_interval)$cf)
  pub_bullet1 <- abm_bullet(label = "Field normalized citations (Cf)", value = cf, reference = 1.0, roundto = 2)
  
  top10_share <- as.numeric(filter(df_cf, interval == last_interval)$top10_share)
  pub_bullet2 <- abm_bullet(label = "Share Top10% publications", value = top10_share, reference = 0.10, pct = TRUE)
  
  grid.arrange(pub_bullet1, pub_bullet2, ncol = 1)
}
```

```{r}
last_interval <- ifelse(df_jcf %>% filter(!is.na(P_frac)) %>% nrow() > 0,
                        nth(df_jcf$interval, -2),
                        "")
```
### **[Journal indicators `r last_interval`](#journal-impact)**  {.no-padding}

```{r, fig.width = 3.5, fig.height = 2}
if(df_jcf %>% filter(!is.na(P_frac)) %>% nrow() > 0){
  jcf <- as.numeric(filter(df_jcf, interval == last_interval)$jcf)
  jour_bullet1 <- abm_bullet(label = "Field normalized journal citations (JCf)", value = jcf, reference = 1.0, roundto = 2)

  top20_share <- as.numeric(filter(df_jcf, interval == last_interval)$top20_share)
  jour_bullet2 <- abm_bullet(label = "Share in Top20% journals", value = top20_share, reference = 0.20, pct = TRUE)
  
  grid.arrange(jour_bullet1, jour_bullet2, ncol = 1)
}

```


```{r}
last_interval <- nth(df_copub$interval, -2)
```
### **[Copublication `r last_interval`](#co-publishing)** {.no-padding}
```{r, fig.width = 3, fig.height = 2}

if(df_copub %>% filter(!is.na(P_full)) %>% nrow > 0){
  nonuniv_share <- as.numeric(filter(df_copub, interval == last_interval)$nonuniv_share)
  nonuniv_lbl <- sprintf("Swedish non-university: %d%%", round(100*nonuniv_share))
  waffle1 <- abm_waffle_pct(nonuniv_share, label = nonuniv_lbl) 

  int_share <- as.numeric(filter(df_copub, interval == last_interval)$int_share)
  int_lbl <- sprintf("International: %d%%", round(100*int_share))
  waffle2 <- 
    abm_waffle_pct(int_share, label = int_lbl)

  grid.arrange(waffle1, waffle2, ncol = 1)
}
```


Row
--------------------------------

### **Notes**
```{r, echo=FALSE, results="asis"}
if (params$is_employee == TRUE)
  cat("<p><b>Bibliometric results for individual researchers should always be treated with caution.</b></p>")

cat("<p>Impact and co-publication indicators are based on Web of Science publications only. ")

if(params$is_employee == FALSE)
  glue("Overall Web of Science coverage for peer reviewed publications in this unit is {100*round(totcov, 3)}%. ",
           "{ifelse(totcov < 0.75, coveragetext(totcov), '')}")

cat("</p>")
```

Row
--------------------------------
### **Background**

The bibliometric indicators referred are based on publications registered in DiVA and published 2012 to 2018. Only publications which have been affiliated to KTH are included. This means that publications written by a researcher before she/he was employed at KTH, and that are not affiliated to KTH, will not be included in the statistics.

Statistics regarding citations and co-publishing are based on the subset of publications in DiVA that are registered in Web of Science.

### **Further information**

- [Guide to the Annual Bibliometric Monitoring at KTH](https://intra.kth.se/bibliometri/public/link/attachment/Guide%20to%20the%20Annual%20Bibliometric%20Monitoring%20at%20KTH.pdf)
- [Description of data, methods and indicators in KTH Annual Bibliometric Monitoring](https://intra.kth.se/bibliometri/public/link/attachment/Description%20of%20data,%20methods%20and%20indicators%20in%20KTH%20Annual%20Bibliometric%20Monitoring.pdf)
- [Formal definitions of field normalized citation indicators at KTH](https://www.kth.se/polopoly_fs/1.544479!/Formal%20definitions%20of%20field%20normalized%20citation%20indicators%20at%20KTH.pdf)
- [Information about DiVA and the registration process - Handle publications in DiVA](https://www.kth.se/en/biblioteket/publicera-analysera/hantera-publikationer)
- [President decision about the Annual Bibliometric Monitoring](https://intra.kth.se/bibliometri/public/link/attachment/Beslut%200934%20Arlig%20bibliometrisk%20uppfoljning.pdf)

Row
----------------------

### **Publication data**

```{r, echo=FALSE, results="asis"}

if (params$embed_data == TRUE) {
  
  library(htmltools)
  
  embed_data <- function(path)
    paste0("data:", mime::guess_type(path), ";base64,", 
      base64enc::base64encode(path))
  
  embed_file_link <- function(path,
    href = embed_data(path),
    name = basename(path),
    text = paste("Download", name), ...) {
    withTags(p(a(text, href = href, download = name, ...)))
  }
  
  icon_download <- htmltools::tag("i", list(
    class = "fa fa-download", 
    paste("Publication data for", unit_label)))
  
  icon_download <- htmltools::attachDependencies(icon_download,
    flexdashboard:::html_dependencies_fonts(TRUE, FALSE))
  
  # export to xlsx format, into tempdir so we can embed a file link
  
  # data that we want to export
  publications_kth <- abm_publications(unit_code = run_unit)
  
  #install.packages("openxlsx")
  library(openxlsx)
  excel_file <- file.path(tempdir(), "PublList_KTH.xlsx")
  write.xlsx(publications_kth, excel_file)
  
  embed_file_link(excel_file,
    title = "Download Publication List in Excel format",
    text = icon_download, 
    class = "btn btn-sm btn-primary")
}
```


```{r, echo=FALSE, results="asis"}

if (params$embed_data == TRUE && params$is_employee == TRUE) {
  out <- '<a href="https://kth.diva-portal.org/dream" class="btn btn-sm btn-primary">Edit your publication data in DiVA</a><p>Please register publications in DiVA as soon as possible for these to be included in the Annual Bibliometric Monitoring.</p>'
  cat(out)
} else {
  cat("Publication data is available only after login.")
}
  
```

### **Attributions**

```{r, echo=FALSE, results="asis"}
wos_disclaimer()
```

Publications in DiVA
=====================================

#### `r unit_label`

Row
---------------------

### **Publication volume, fractionalized**

```{r}
if(nrow(df_diva) > 0)
  DT::datatable(df_diva %>% rename("WoS coverage" = "WoS_coverage",
                                   "DiVA publication type" = "Publication_Type_DiVA",
                                   "Total" = "P_frac"),
                rownames = FALSE,
                extensions = "Buttons",
                options = list(
                  bPaginate = FALSE,
                  pageLength = 100,
                  dom = 'Bt',
                  buttons = c("copy", "csv", "excel"),
                  title = "ABM_publications")
                ) %>%
    formatRound(2:9, digits = 1, mark = "") %>%
    formatPercentage("WoS coverage", digits = 1) %>%
    abm_format_rows()

```

Row
---------------------

### **Publication volume**
```{r, fig.width=10, fig.height=5}
if(nrow(df_diva) > 0)
  abm_graph_diva(df_diva)
```

### **Web of Science coverage**

```{r, fig.width=8, fig.height=5}
if(nrow(df_diva) > 0)
  abm_graph_wos_coverage(df_diva)
```

Citation impact
=====================================

#### `r unit_label`

Row
---------------------

### **Citations 3-year window, fractional counts**

```{r}
if(nrow(df_cit3y) > 0)
  DT::datatable(df_cit3y %>% rename("Publication year" = "Publication_Year_ch",
                                    "Publications" = "P_frac",
                                    "Total Citations" = "C3_frac",
                                    "Average Citations" = "C3"),
                rownames = FALSE,
                extensions = "Buttons",
                options = list(
                  bPaginate = FALSE,
                  dom = 'Bt',
                  buttons = c("copy", "csv", "excel"),
                  title = "ABM_citations")
                ) %>% 
    formatRound(2:4, digits = 1, mark = "") %>%
    abm_format_rows()
```

### **Field normalized citations - Fractionalized (3-year moving average)**

```{r}
if(nrow(df_cf) > 0)
  DT::datatable(df_cf %>% rename("Publication years" = "interval",
                                 "Publications" = "P_frac",
                                 "Average Cf" = "cf",
                                 "Top 10% publications" = "top10_count",
                                 "Share Top 10%" = "top10_share"),
                rownames = FALSE,
                extensions = "Buttons",
                options = list(
                  bPaginate = FALSE,
                  dom = 'Bt',
                  buttons = c("copy", "csv", "excel"),
                  filename = "ABM_field_normalized_citations")
                ) %>% 
    formatRound(c(2, 4), digits = 1, mark = "") %>% 
    formatRound(3, digits = 2, mark = "") %>%
    formatPercentage(5, digits = 1) %>%
    abm_format_rows()
```

Row
--------------------

### **Notes**
```{r, echo=FALSE, results="asis"}
cat("<p>This table is based on Web of Science publication types Article, Proceedings paper, Review, Letter and Editorial.</p>")

years <- df_cit3y %>% filter(substr(Publication_Year_ch, 1, 1) == "2") %>% pull(Publication_Year_ch) %>% as.integer()
mincov <- df_woscov %>% filter(Publication_Type == "Peer reviewed" & Publication_Year %in% years) %>% pull(woscov_frac) %>% min()
minpubs <- df_woscov %>% filter(Publication_Type == "Peer reviewed" & Publication_Year %in% years) %>% pull(sumcov_full) %>% min()

cat(glue("<p>Rows in this table are based on at least {minpubs} (full counted) publications ",
         "and have a Web of Science coverage of at least {round(100*mincov, 1)}%.<br>",
         "(DiVA publication types Article, peer review and Conference paper, peer review)</p>"))

if(minpubs < 50)
  cat("<p><b>Indicators based on < 50 publications are considered unreliable</b></p>")

if(mincov < 0.75)
  cat("<p>", coveragetext(mincov), "</p>")
```

### **Notes**
```{r, echo=FALSE, results="asis"}
cat("<p>This table is based on Web of Science publication types Article and Review.</p>")

intervals <- df_cf %>% filter(substr(interval, 1, 1) == "2") %>% pull(interval)
woscov_cf <- df_woscov %>%
  filter(Publication_Type == "Article, peer review")
woscov_cf <- woscov_cf %>% 
  inner_join(sliding_intervals(min(woscov_cf$Publication_Year), max(woscov_cf$Publication_Year), 3), by = c("Publication_Year" = "x")) %>%
  filter(interval %in% intervals) %>%
  group_by(interval) %>% 
  summarise(woscov_frac = sum(sumcov_frac) / sum(p_frac),
            sumcov_full = sum(sumcov_full))

mincov <- min(woscov_cf$woscov_frac)
minpubs <- min(woscov_cf$sumcov_full)

cat(glue("<p>Rows in this table are based on at least {minpubs} (full counted) publications ",
         "and have a Web of Science coverage of at least {round(100*mincov, 1)}%.<br>",
         "(DiVA publication type Article, peer review)</p>"))

if(minpubs < 50)
  cat("<p><b>Indicators based on < 50 publications are considered unreliable</b></p>")

if(mincov < 0.75)
  cat("<p>", coveragetext(mincov), "</p>")

```


Row
---------------------

### **Average field normalized citations (Cf)**

```{r}
if(df_cf %>% filter(!is.na(P_frac)) %>% nrow > 0)
  abm_graph_cf(df_cf)
```


### **Share Top 10%**

```{r}
if(df_cf %>% filter(!is.na(P_frac)) %>% nrow > 0)
  abm_graph_top10(df_cf)
```


Journal impact
=====================================

#### `r unit_label`

Row
---------------------

### **3-year moving average, fractional counts**

```{r}
if(nrow(df_jcf) > 0)
  DT::datatable(df_jcf %>% rename("Publication years" = "interval",
                                  "Publications" = "P_frac",
                                  "Average Journal Cf" = "jcf",
                                  "Publications in Top 20% journals" = "top20_count",
                                  "Share Top 20% journals" = "top20_share"),
                rownames = FALSE,
                extensions = "Buttons",
                options = list(
                  bPaginate = FALSE,
                  dom = 'Bt',
                  buttons = c("copy", "csv", "excel"),
                  title = "ABM_journal_impact")
                ) %>% 
    formatRound(c(2, 4), digits = 1, mark = "") %>% 
    formatRound(3, digits = 2, mark = "") %>% 
    formatPercentage(5, digits = 1) %>%
    abm_format_rows()
```

Row
-----------------

### **Notes**
```{r, echo=FALSE, results="asis"}
cat("<p>This table is based on Web of Science publication types Article and Review.</p>")

intervals <- df_jcf %>% filter(substr(interval, 1, 1) == "2") %>% pull(interval)
woscov_jcf <- df_woscov %>%
  filter(Publication_Type == "Article, peer review")
woscov_jcf <- woscov_jcf %>% 
  inner_join(sliding_intervals(min(woscov_jcf$Publication_Year), max(woscov_jcf$Publication_Year), 3), by = c("Publication_Year" = "x")) %>%
  filter(interval %in% intervals) %>%
  group_by(interval) %>% 
  summarise(woscov_frac = sum(sumcov_frac) / sum(p_frac),
            sumcov_full = sum(sumcov_full))

mincov <- min(woscov_cf$woscov_frac)
minpubs <- min(woscov_cf$sumcov_full)

cat(glue("<p>Rows in this table are based on at least {minpubs} (full counted) publications ",
         "and have a Web of Science coverage of at least {round(100*mincov, 1)}%.<br>",
         "(DiVA publication type Article, peer review)</p>"))

if(minpubs < 50)
  cat("<p><b>Indicators based on < 50 publications are considered unreliable</b></p>")

if(mincov < 0.75)
  cat("<p>", coveragetext(mincov), "</p>")

```

Row
---------------------

### **Field normalized journal indicator (JCf)**

```{r}
if(df_jcf %>% filter(!is.na(P_frac)) %>% nrow > 0)
  abm_graph_jcf(df_jcf)
```


### **Share Journal Top 20%**

```{r}
if(df_cf %>% filter(!is.na(P_frac)) %>% nrow > 0)
  abm_graph_top20(df_jcf)
```

Co-publishing
=====================================

#### `r unit_label`

Row
---------------------

### **International and Swedish non-university copublications (full counts)**

```{r}
if(nrow(df_copub) > 0)
  DT::datatable(df_copub %>% rename("Publication years" = "interval",
                                   "Publications" = "P_full",
                                   "Swedish non-university copublications" = "nonuniv_count",
                                   "Share Swedish non-university" = "nonuniv_share",
                                   "International copublications" = "int_count",
                                   "Share international" = "int_share"),
                rownames = FALSE,
                extensions = "Buttons",
                options = list(
                  bPaginate = FALSE,
                  dom = 'Bt',
                  buttons = c("copy", "csv", "excel"),
                  title = "ABM_copublications")
                ) %>%
    formatPercentage(c(4,6), digits = 1) %>%
    abm_format_rows()
```

Row
-----------------

### **Notes**
```{r, echo=FALSE, results="asis"}
cat("<p>This table is based on Web of Science publication types Article and Review.</p>")

intervals <- df_copub %>% filter(substr(interval, 1, 1) == "2") %>% pull(interval)
woscov_copub <- df_woscov %>%
  filter(Publication_Type == "Article, peer review")
woscov_copub <- woscov_copub %>% 
  inner_join(sliding_intervals(min(woscov_copub$Publication_Year), max(woscov_copub$Publication_Year), 3), by = c("Publication_Year" = "x")) %>%
  filter(interval %in% intervals) %>%
  group_by(interval) %>% 
  summarise(woscov_full = sum(sumcov_full) / sum(p_full))

mincov <- min(woscov_copub$woscov_full)
minpubs <- min(df_copub$P_full)

cat(glue("<p>Rows in this table are based on at least {minpubs} (full counted) publications ",
         "and have a Web of Science coverage of at least {round(100*mincov, 1)}%.<br>",
         "(DiVA publication type Article, peer review)</p>"))

if(minpubs < 50)
  cat("<p><b>Indicators based on < 50 publications are considered unreliable</b></p>")

if(mincov < 0.75)
  cat("<p>", coveragetext(mincov), "</p>")
```

Row
-------

### **International and Swedish non-university copublication**

```{r, fig.width=6, fig.height=4}
if(df_copub %>% filter(!is.na(P_full)) %>% nrow > 0)
  abm_graph_copub(df_copub)

```
