---
title: "ABM"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    favicon: KTH_logo_RGB_svart.png
    fig_mobile: FALSE
params:
  unit_code: !r bibliomatrix:::abm_config()$default_unit
  is_employee: FALSE
  use_package_data: TRUE
  embed_data: FALSE
---

```{css echo=FALSE}
@font-face {
  font-family: 'Figtree';
  font-style: normal;
  font-weight: 400;
  src: url('fonts/figtree-v5-latin_latin-ext-regular.woff2') format('woff2');
}

body {
  font-family: 'Figtree';
}
```


```{r setup, include=FALSE}
# unit_codes for testing:
# 
# u1g9umtq
# u1jr9fll 
# u1ygqmuy
# u13bp6vd
# u18qe64m
# u1o2ujjd

library(flexdashboard)
library(DT)
library(readr)
library(purrr)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(bibliomatrix)
library(tidyr)
library(scales)
#library(plotly)
library(kableExtra)
library(glue)
library(extrafont)
library(kthapi)
library(DBI)
library(ktheme)

colors_vb <- palette_kth_neo(17)

# Retrieve result tables to use in tabs and key indicators

data <- data.frame()

if (params$embed_data || !params$use_package_data) {
  con <- con_bib()
  data <- abm_data(
    con = con,
    unit_code = params$unit_code,
    pub_year = abm_config()$start_year:abm_config()$stop_year,
    analysisId = abm_config()$analysis_id
    ) %>% collect()
  dbDisconnect(con)
}

if (params$use_package_data != TRUE) {
  df_diva <- abm_table1(data)
  df_diva_full <- abm_table1_full(data)
  df_cit3y <- abm_table2(data)
  df_cf <- abm_table3(data)
  df_jcf <- abm_table4(data)
  df_copub <- abm_table5(data)
  df_oa <- abm_table6(data)
  df_scop_cit <- abm_table_scop_cit(data)
  df_scop_normcit <- abm_table_scop_normcit(data)
  df_scop_snip <- abm_table_scop_snip(data)
  df_scop_copub <- abm_table_scop_copub(data)
  df_coverage <- abm_coverage(data)
  con <- con_bib()
  unit_meta <- unit_info(con = con) %>% filter(unit_code == params$unit_code)
  df_copub_countries <- abm_copub_countries(con = con,
                                            unit_level = ifelse(isTRUE(unit_meta$org_level >= 0),
                                                                unit_meta$org_level, 3),
                                            unit_code = params$unit_code,
                                            analysisId = abm_config()$analysis_id,
                                            analysis_start = abm_config()$start_year,
                                            analysis_stop = abm_config()$stop_year)
  df_copub_orgs <- abm_copub_orgs(con = con,
                                  unit_level = ifelse(isTRUE(unit_meta$org_level >= 0),
                                                      unit_meta$org_level, 3),
                                  unit_code = params$unit_code,
                                  analysisId = abm_config()$analysis_id,
                                  analysis_start = abm_config()$start_year,
                                  analysis_stop = abm_config()$stop_year)
  df_sdg_year <- abm_sdg_year(con = con,
                              data = data,
                              analysisId = abm_config()$analysis_id,
                              analysis_start = abm_config()$start_year,
                              analysis_stop = abm_config()$stop_year)
  df_sdg_table <- abm_sdg_table(con = con,
                                data = data,
                                analysisId = abm_config()$analysis_id,
                                analysis_start = abm_config()$start_year,
                                analysis_stop = abm_config()$stop_year)
  dbDisconnect(con)
} else {
  df_diva <- pluck(abm_public_kth$units, params$unit_code, "diva")
  df_diva_full <- pluck(abm_public_kth$units, params$unit_code, "diva_full")
  df_cit3y <- pluck(abm_public_kth$units, params$unit_code, "wos_cit3y")
  df_cf <- pluck(abm_public_kth$units, params$unit_code, "wos_cf")
  df_jcf <- pluck(abm_public_kth$units, params$unit_code, "wos_jcf")
  df_copub <- pluck(abm_public_kth$units, params$unit_code, "wos_copub")
  df_copub_countries <- pluck(abm_public_kth$units, params$unit_code, "wos_copub_countries")
  df_copub_orgs <- pluck(abm_public_kth$units, params$unit_code, "wos_copub_orgs")
  df_oa <- pluck(abm_public_kth$units, params$unit_code, "oa")
  df_scop_cit <- pluck(abm_public_kth$units, params$unit_code, "scop_cit")
  df_scop_normcit <- pluck(abm_public_kth$units, params$unit_code, "scop_normcit")
  df_scop_snip <- pluck(abm_public_kth$units, params$unit_code, "scop_snip")
  df_scop_copub <- pluck(abm_public_kth$units, params$unit_code, "scop_copub")
  df_coverage <- pluck(abm_public_kth$units, params$unit_code, "coverage")
  df_sdg_year <- pluck(abm_public_kth$units, params$unit_code, "scop_sdg_year")
  df_sdg_table <- pluck(abm_public_kth$units, params$unit_code, "scop_sdg_table")
  unit_meta <- filter(abm_public_kth$meta, unit_code == params$unit_code)
}

unit_level <- unit_meta %>% pull(org_level)
  
if(isTRUE(unit_level >= 0)){
  
  unit_label <- 
    abm_public_kth$meta %>% 
    filter(unit_code == params$unit_code) %>%
    pull(unit_long_en)
  
} else {
  
  unit_label <- 
    kth_displayname(user = params$unit_code, "kthid")
}

#unit_label <- paste0("Annual Bibliometric Monitoring: ", unit_label)



current_date <- format(Sys.Date(), "%Y%m%d")

abm_unit_title <- paste0("ABM: ", unit_label)

STATIC <- "https://kth-library.github.io/abm"
```

<style>
<!-- TODO: this does not work in responsive mobile mode -->
.navbar-header {
  width: 0px;
  visibility: hidden;
}
.nav-tabs-custom > .nav-tabs > li > a {
  font-size: 1.5rem
}
.navbar {
  background-color:#004791;
}
</style>


Overview
===========================

#### `r unit_label`

Row  {data-height=240}
---------------------

```{r}
  yrfields <- grep("^[1-2][0-9]{3}$", names(df_diva), value = TRUE)
  firstyear <- min(yrfields)
  lastyear <- max(yrfields)
  
  as_range <- function(x, delim = "-") {
    y <- as.integer(x)
    paste(collapse = delim, na.omit(dplyr::case_when(
      is.finite(y) ~ y
    )))
  }
```

### **Publications in DiVA `r as_range(lastyear)`<br>(fractional counts)**

```{r, fig.width = 1.75, fig.height = 2}
abm_ui_valuebox_publications(df_diva, lastyear, colors_vb[1], unit_label)
```

### **WoS coverage `r as_range(c(firstyear, lastyear))`<br>(peer reviewed)**

```{r, fig.width = 1.75, fig.height = 2}
abm_ui_valuebox_coverage(df_coverage, colors_vb[1], "wos", unit_label)
```

### **Scopus coverage `r as_range(c(firstyear, lastyear))`<br>(peer reviewed)**

```{r, fig.width = 1.75, fig.height = 2}
abm_ui_valuebox_coverage(df_coverage, colors_vb[1], "scopus", unit_label)
```

```{r}
has_rows <- df_cf %>% filter(!is.na(P_frac)) %>% nrow() > 0
last_interval <- ifelse(has_rows, paste((as.numeric(nth(df_cf$Publication_Year, -2))-2),nth(df_cf$Publication_Year, -2), sep = "-"), "")
```

### **[Citation impact `r last_interval` (WoS)](#citation-impact)** {.no-padding .no-mobile}

```{r, fig.width = 3.7, fig.height = 2}
abm_ui_bullet_citations(df_cf)
```

### **[Citation impact `r last_interval` (WoS)](#citation-impact)** {.no-padding .mobile}

```{r, fig.width=3.75, fig.height = 2}
abm_ui_bullet_citations(df_cf)
```

```{r}

has_rows <- df_jcf %>% filter(!is.na(P_frac)) %>% nrow() > 0
last_interval <- ifelse(has_rows, paste((as.numeric(nth(df_jcf$Publication_Year, -2))-2),nth(df_jcf$Publication_Year, -2), sep = "-"), "")
```
### **[Journal impact `r last_interval` (WoS)](#journal-impact)**  {.no-padding .no-mobile}

```{r, fig.width=3.8, fig.height = 2} 
abm_ui_bullet_journal(df_jcf)
```

### **[Journal impact `r last_interval` (WoS)](#journal-impact)**  {.no-padding .mobile}

```{r, fig.width=3.75, fig.height = 2}
abm_ui_bullet_journal(df_jcf)
```


```{r}
has_rows <- df_copub %>% filter(!is.na(P_full)) %>% nrow > 0
last_interval <- ifelse(has_rows, paste((as.numeric(nth(df_copub$Publication_Year, -2))-2),nth(df_copub$Publication_Year, -2), sep = "-"), "")
```

### **[Co&#8209;publishing `r last_interval` (WoS)](#co&#8209;publishing)** {.no-padding .no-mobile}
```{r, fig.width=3.75, fig.height = 2}
abm_ui_waffle_copub(df_copub)
```

### **[Co&#8209;publishing `r last_interval` (WoS)](#co&#8209;publishing)** {.no-padding .mobile}

```{r, fig.width=2.75, fig.height = 2}
abm_ui_waffle_copub(df_copub)
```

Row
--------------------------------

### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.html#overview){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis"}
woscov <- df_coverage %>% 
    filter(Publication_Type == "Peer reviewed") %>% 
    summarise(woscov = sum(sumwos_frac) / sum(p_frac)) %>% 
    pull(woscov)

cat("<p>Indicators in the Citation impact, Journal impact and Co&#8209;publishing tabs are based on Web of Science publications only. Corresponding Scopus indicators can be found under the Scopus tab.</p>")

if(isTRUE(unit_level >= 0)){

  #<span title='mytitle' onclick=\"window.location.href='https://KTH-Library.github.io/abm/ABM_guide.pdf';\" style='cursor: pointer;></span>'
  glue("<p><span title='Legend: 75% or above is good, 60% or above is moderate while lower than 60% is poor'>Overall Web of Science coverage for peer reviewed publications in this unit is ",
       "{coveragetext(woscov)}, {100*round(woscov, 3)}%.</span></p>")

} else {

  cat("<p><b>Bibliometric results for individual researchers should always be interpreted with caution. </b></br/>
      Bibliometric indicators work best at an aggregated level, and at the individual level 
      the publication profile of researchers, their collaboration networks and their subject specialization may 
      interact with e.g. the field-normalization of citation indicators. The relatively low publication volume of 
      individuals also makes indicator averages very unreliable. </p>")

}

cat("<p>Note that the coverage numbers for Web of Science and Scopus apply to publications in the KTH bibliometric database Bibmet. If a WoS-id or Scoupus-id from DiVA can not be matched in Bibmet, it does not count as covered.</p>")
```

Row
--------------------------------
### **Background**

The bibliometric indicators referred are based on publications registered in DiVA and published `r abm_config()$start_year` to `r abm_config()$stop_year`. Only publications which have been affiliated to KTH are included. This means that publications written by a researcher before she/he was employed at KTH, and that are not affiliated to KTH, will not be included in the statistics.

Statistics regarding citations and co&#8209;publishing are based on the subset of publications in DiVA that are registered in Web of Science (Citation impact, Journal impact and Co&#8209;publishing tabs) or Scopus (Scopus tab).

Row
--------------------------------
### **Publication data**

```{r, echo=FALSE}

# download button for publication list
unit_file_label <- params$unit_code
if (isTRUE(unit_level == 1)){
  unit_file_label <- 
    unit_info() %>% 
    filter(unit_code == params$unit_code) %>% 
    pull(unit_short)
}

abm_ui_button_publist(
  data = data,
  is_loggedin = params$embed_data,
  unit_label = unit_label,
  unit_code = params$unit_code,
  unit_file_label = unit_file_label,
  is_authorbased = FALSE
)

# DiVA Dream Portal button
if (params$is_employee == TRUE) {
  abm_ui_button_diva()
}
```

Publication summary
=====================================

#### `r unit_label`

Row {.tabset data-height=700}
---------------------

### Fractional count
#### **Publication volume, fractionalized** {.no-padding .no-mobile}

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>


```{r}
abm_ui_datatable_diva(
  df_diva,
  unit_file_label = unit_file_label,
  unit_title = abm_unit_title
)

```

#### **Publication volume, fractionalized** {.no-padding .mobile}

```{r, fig.width=3.75}
abm_ui_kable_diva(df_diva)
```

### Full count
#### **Publication volume, full count** {.no-padding .no-mobile}

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>

```{r}

abm_ui_datatable_diva_full(
  df_diva_full, 
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)

```

#### **Publication volume, full count** {.no-padding .mobile}

```{r, fig.width=3.75}
abm_ui_kable_diva_full(df_diva_full)
```

Row 
---------------------

### **Publication volume** {.no-padding .no-mobile}

```{r, fig.width=8, fig.height=5}
if (nrow(df_diva) > 0) {
  p <- abm_graph_diva(df_diva)
  p
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```

### **Publication volume** {.no-padding .mobile}

```{r, fig.width=8, fig.height = 5}
if (nrow(df_diva) > 0) {
  p
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
``` 

### **Web of Science coverage by publication type** {.no-padding .no-mobile}

```{r, fig.width=6, fig.height=5}
if (nrow(df_diva %>% left_join(get_pubtype_order(), by = c("Publication_Type_DiVA" = "diva_publication_type")) %>% filter(WoS_coverage != 0)) > 0) {
  p <- abm_graph_wos_coverage(df_diva)
  p
} else {
  shiny::HTML("<p><i>There are no data available for this graph</i></p>")
}
```

### **Web of Science coverage by publication type** {.no-padding .mobile}

```{r, fig.width=6, fig.height=5}
if (nrow(df_diva) > 0) {
  p
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```


Citation impact
=====================================

#### `r unit_label`


Row
---------------------

### **Average field normalized citations (Cf)**

```{r, fig.width=8, fig.height=4}
if (df_cf %>% filter(!is.na(P_frac)) %>% nrow() > 0){
  abm_graph_cf(df_cf)
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```


### **Share of publications among Top 10% cited**

```{r, fig.width=8, fig.height=4}
if (df_cf %>% filter(!is.na(P_frac)) %>% nrow() > 0){
  abm_graph_top10(df_cf)
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```


Row {data-height=550}
---------------------

### **Citations 3-year window, fractional counts** {.no-mobile}

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>
```{r}
abm_ui_datatable_city3y(
  df_cit3y, 
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)
```

### **Citations 3-year window, fractional counts** {.mobile}

```{r}
abm_ui_kable_cit3y(df_cit3y)
```

### **Field normalized citations, fractionalized (3-year moving average)** {.no-mobile}

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>

```{r}
abm_ui_datatable_cf(
  df_cf,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)
```

### **Field normalized citations, fractionalized (3-year moving average)** {.no-padding .mobile}

```{r}
abm_ui_kable_cf(df_cf)
```


Row
--------------------

### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.html#citation-impact){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis"}
cat("This table is based on Web of Science publication types Article, Proceedings paper, Review, Letter and Editorial.<br>")

if(isTRUE(unit_level >= 0)){

  years <- df_cit3y %>% filter(substr(Publication_Year_ch, 1, 1) == "2") %>% pull(Publication_Year_ch) %>% as.integer()
  mincov <- df_coverage %>% filter(Publication_Type == "Peer reviewed" & Publication_Year %in% years) %>% pull(woscov_frac) %>% min()
  minpubs <- df_coverage %>% filter(Publication_Type == "Peer reviewed" & Publication_Year %in% years) %>% pull(sumwos_full) %>% min()

  cat(glue("<span title='Legend: 75% or above is good, 60% or above is moderate while lower than 60% is poor'>Rows are based on at least <b>{minpubs}</b> (full counted) publications with ",
           "<b>{coveragetext(mincov)}</b> Web of Science coverage (at least <b>{round(100*mincov, 1)}%</b>).<br>",
           "(DiVA publication types Article, peer review and Conference paper, peer review)<br></span>"))

  if(minpubs < 50)
    cat("<b>Indicators based on < 50 publications are considered unreliable</b>")

} else {

  cat("<b>Bibliometric results for individual researchers should always be interpreted with caution.</b>")

}
```

### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.html#citation-impact){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis"}
cat("This table is based on Web of Science publication types Article and Review.<br>")

if(isTRUE(unit_level >= 0)){

  woscov_cf <- df_coverage %>%
    filter(Publication_Type == "Article, peer review", Publication_Year %in% df_cf$Publication_Year)

  mincov <- min(woscov_cf$woscov_frac)
  minpubs <- min(woscov_cf$sumwos_full)

  cat(glue("<span title='Legend: 75% or above is good, 60% or above is moderate while lower than 60% is poor'>Rows are based on at least <b>{minpubs}</b> (full counted) publications with ",
           "<b>{coveragetext(mincov)}</b> Web of Science coverage (at least <b>{round(100*mincov, 1)}%</b>).<br>",
           "(DiVA publication type Article, peer review)<br></span>"))

  if(minpubs < 50)
    cat("<b>Indicators based on < 50 publications are considered unreliable</b>")

} else {

  cat("<b>Bibliometric results for individual researchers should always be interpreted with caution.</b>")

}
```


Journal impact
=====================================

#### `r unit_label`

Row
---------------------

### **Field normalized journal impact (JCf)**

```{r, fig.width=9, fig.height=4}
if(df_jcf %>% filter(!is.na(P_frac)) %>% nrow() > 0) {
  abm_graph_jcf(df_jcf)
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```


### **Share of publications in Top 20% journals**

```{r, fig.width=9, fig.height=4}
if(df_cf %>% filter(!is.na(P_frac)) %>% nrow() > 0) {
  abm_graph_top20(df_jcf)
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```

Row {data-height=550}
---------------------

### **Journal impact, fractionalized (3-year moving average)** {.no-mobile}

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>

```{r}
abm_ui_datatable_jcf(
  df_jcf,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)
```

### **Journal impact, fractionalized (3-year moving average)** {.no-padding .mobile}

```{r, fig.width=3.75}
abm_ui_kable_jcf(df_jcf)
```

Row
-----------------

### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.html#journal-impact){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis"}
cat("This table is based on Web of Science publication types Article and Review.<br>")

if(isTRUE(unit_level >= 0)){
  woscov_jcf <- df_coverage %>%
    filter(Publication_Type == "Article, peer review", Publication_Year %in% df_jcf$Publication_Year)

  mincov <- min(woscov_jcf$woscov_frac)
  minpubs <- min(woscov_jcf$sumcov_full)

  cat(glue("<span title='Legend: 75% or above is good, 60% or above is moderate while lower than 60% is poor'>Rows are based on at least <b>{minpubs}</b> (full counted) publications with ",
           "<b>{coveragetext(mincov)}</b> Web of Science coverage (at least <b>{round(100*mincov, 1)}%</b>).<br>",
           "(DiVA publication type Article, peer review)<br></span>"))

  if(minpubs < 50)
    cat("<b>Indicators based on < 50 publications are considered unreliable</b>")

} else {

  cat("<b>Bibliometric results for individual researchers should always be interpreted with caution.</b>")

}
```

Co&#8209;publishing {data-orientation=rows}
=====================================

#### `r unit_label`

Row {.tabset data-height=1400}
---------------------

### Summary

<div style='display:flex; flex-direction:column; justify-content:space-evenly; align-items:center;'>

##### **International and Swedish non-university co&#8209;publication**
```{r, fig.width=9, fig.height=4}
if(df_copub %>% filter(!is.na(P_full)) %>% nrow() > 0) {
  abm_graph_copub(df_copub)
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```

</div>

##### **International and Swedish non-university co&#8209;publications (full counts)** {.no-mobile}

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>

```{r, fig.height=4}
abm_ui_datatable_copub(
  df_copub,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)
```

##### **International and Swedish non-university co&#8209;publications (full counts)** {.no-padding .mobile}

```{r}
abm_ui_kable_copub(df_copub)
```


##### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.html#co-publishing){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis"}
cat("<hr>")
cat("This table is based on Web of Science publication types Article and Review.<br>")

if(isTRUE(unit_level >= 0)){
  woscov_copub <- df_coverage %>%
    filter(Publication_Type == "Article, peer review", Publication_Year %in% df_copub$Publication_Year)

  mincov <- min(woscov_copub$woscov_full)
  minpubs <- min(df_copub$P_full)

  cat(glue("<span title='Legend: 75% or above is good, 60% or above is moderate while lower than 60% is poor'>Rows are based on at least <b>{minpubs}</b> (full counted) publications with ",
           "<b>{coveragetext(mincov)}</b> Web of Science coverage (at least <b>{round(100*mincov, 1)}%</b>).<br>",
           "(DiVA publication type Article, peer review)<br></span>"))

  if(minpubs < 50)
    cat("<b>Indicators based on < 50 publications are considered unreliable</b>")

} else {

  cat("<b>Bibliometric results for individual researchers should always be interpreted with caution.</b>")

}
cat("<hr>")
```

### Countries and organizations

##### **Co&#8209;publication countries** {.no-mobile}
<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
table.dataTable thead .sorting_asc, .sorting_desc, .sorting {
    background-image: none !important;
}
</style>

```{r}
abm_ui_datatable_copub_countries(
  df_copub_countries,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
) 
```

##### **Co&#8209;publication countries** {.no-padding .mobile}
```{r}
abm_ui_kable_copub_countries(df_copub_countries) 
```


##### **Co&#8209;publication organizations** {.no-mobile}

```{r}
abm_ui_datatable_copub_orgs(
  df_copub_orgs,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
) 
```

##### **Co&#8209;publication countries** {.no-padding .mobile}
```{r}
abm_ui_kable_copub_orgs(df_copub_orgs) 
```

Open Access
=====================================

#### `r unit_label`

Row
---------------------

### **Overview of Open Access publications - piechart** 

```{r, fig.width=8}
if (df_oa %>% filter(!is.na(P_tot)) %>% nrow() > 0) {
  abm_graph_oadata_piechart(df_oa, type = "ggplot")
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```

### **Stacked area chart for publications**

```{r, fig.width=8}
if (df_oa %>% filter(!is.na(P_tot)) %>% nrow() > 0) {
  abm_graph_oadata_stackedarea(df_oa)
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```

Row {data-height=550}
---------------------

### **Open Access publications, full counts** {.no-mobile}
<!-- The DT table headers may have a right alignment issue due to some whitespace issue artifact from disabled sorting? -->
<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
.table th {
  text-align: right;
}
</style>

```{r}
abm_ui_datatable_oa(
  df_oa,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)

```

### **Open Access publications, full counts** {.no-padding .mobile}

```{r, fig.width=3.75}
abm_ui_kable_oa(df_oa)
```

Row
-------

### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.html#open-access){target="_blank" style="position:relative;float:right;"}

The Open Access type of the publications was fetched from the [Unpaywall REST API](https://unpaywall.org/products/api). The method to determine the OA type is presented [here](https://support.unpaywall.org/support/solutions/articles/44001777288-what-do-the-types-of-oa-status-green-gold-hybrid-and-bronze-mean-).

In summary, the different OA types can be described as follows:

- *Diamond*: The full text has been found on a publisher website, there is no article publication cost.

- *Gold:* The full text has been found on a publisher website, in a journal that is fully OA.

- *Hybrid:* The full text has been found on a publisher website, in a journal that is not fully OA.

- *Green:* The full text has been found in an institutional repository, such as DiVA.

**N.B.**: This table is based on peer-reviewed publications for which Unpaywall could determine the OA type (necessary condition: have a DOI number). Unpaywall's method is empirical and does not strictly equate to copyright license. As a consequence, the OA status of a given publication may vary with time --- for example turning from *"Not OA"* to *"Green"* when a full text is added to DiVA.


Scopus
=====================================

#### `r unit_label`

Row {.tabset data-height=1800}
-----------------------------------------------------------------------

### Citation Impact

<div style='display:flex; flex-direction:row; justify-content:space-evenly; align-items:stretch;'>
<div>
##### **Average field weighted citation impact (FWCI)**

```{r, fig.height = 4, fig.width = 6}
if(df_scop_normcit %>% filter(!is.na(P_frac)) %>% nrow() > 0) {
  abm_graph_scop_normcit(df_scop_normcit)
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```
</div>

<div style='margin:10px'></div>

<div>
##### **Share of publications among Top 10% cited**

```{r, fig.height = 4, fig.width = 6}
if(df_scop_normcit %>% filter(!is.na(P_frac)) %>% nrow() > 0) {
  abm_graph_scop_top10(df_scop_normcit)
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```
</div>
</div>

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>

##### **Citations, open window** {.no-mobile}

```{r}
abm_ui_datatable_scop_cit(
  df_scop_cit,
  unit_file_label = unit_file_label,
  unit_title = abm_unit_title
)
```

##### **Citations, open window** {.mobile}

```{r}
abm_ui_kable_scop_cit(df_scop_cit)
```

##### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.html#scopus){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis", fig.width=6}
cat("<hr>")
cat("This table is based on Scopus publication types Article, Conference Paper, Review, Letter and Editorial.<br>")
if(isTRUE(unit_level >= 0)){
  years <- df_scop_cit %>% filter(substr(Publication_Year_ch, 1, 1) == "2") %>% pull(Publication_Year_ch) %>% as.integer()
  mincov <- df_coverage %>% filter(Publication_Type == "Peer reviewed" & Publication_Year %in% years) %>% pull(scopcov_frac) %>% min()
  minpubs <- df_coverage %>% filter(Publication_Type == "Peer reviewed" & Publication_Year %in% years) %>% pull(sumscop_full) %>% min()
  cat(glue("<span title='Legend: 75% or above is good, 60% or above is moderate while lower than 60% is poor'>Rows are based on at least <b>{minpubs}</b> (full counted) publications with ",
           "<b>{coveragetext(mincov)}</b> Scopus coverage (at least <b>{round(100*mincov, 1)}%</b>).<br>",
           "(DiVA publication types Article, peer review and Conference paper, peer review)<br></span>"))
  if(minpubs < 50)
    cat("<b>Indicators based on < 50 publications are considered unreliable</b>")
} else {
  cat("<b>Bibliometric results for individual researchers should always be interpreted with caution.</b>")
}
cat("<hr>")
```

##### **Field weighted citation impact (FWCI)** {.no-mobile}

```{r}
abm_ui_datatable_scop_normcit(
  df_scop_normcit,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)
```

##### **Field weighted citation impact (FWCI)** {.mobile}

```{r}
abm_ui_kable_scop_normcit(df_scop_normcit)
```


##### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.html#scopus){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis", fig.width=6}
cat("<hr>")
cat("This table is based on Scopus publication types Article, Review and Conference Paper.<br>")
if(isTRUE(unit_level >= 0)){
  scopcov_normcit <- df_coverage %>%
    filter(Publication_Type == "Peer reviewed", Publication_Year %in% df_scop_normcit$Publication_Year)

  mincov <- min(scopcov_normcit$scopcov_frac)
  minpubs <- min(scopcov_normcit$sumscop_full)
  
  cat(glue("<span title='Legend: 75% or above is good, 60% or above is moderate while lower than 60% is poor'>Rows are based on at least <b>{minpubs}</b> (full counted) publications with ",
           "<b>{coveragetext(mincov)}</b> Scopus coverage (at least <b>{round(100*mincov, 1)}%</b>).<br>",
           "(DiVA publication types Article, peer review and Conference paper, peer review)<br></span>"))
  if(minpubs < 50)
    cat("<b>Indicators based on < 50 publications are considered unreliable</b>")
} else {
  cat("<b>Bibliometric results for individual researchers should always be interpreted with caution.</b>")
}
cat("<hr>")
```

### Journal Impact

<div style='display:flex; flex-direction:row; justify-content:space-evenly; align-items:stretch;'>
<div>

##### **Field normalized journal impact (SNIP)**

```{r, fig.height = 4, fig.width = 6}
if(df_scop_snip %>% filter(!is.na(P_frac)) %>% nrow() > 0) {
  abm_graph_scop_snip(df_scop_snip)
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```  
</div>

<div style='margin:10px'></div>

<div>
##### **Share of publications in Top 20% journals**

```{r, fig.height = 4, fig.width = 6}
if(df_scop_snip %>% filter(!is.na(P_frac)) %>% nrow() > 0) {
  abm_graph_scop_top20(df_scop_snip)
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```  
</div>
</div>

<div style='display:flex; flex-direction:column; justify-content:space-evenly; align-items:stretch;'>

##### **Journal impact, fractionalized (3-year moving average)** {.no-mobile}

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>

```{r, fig.height=4}
abm_ui_datatable_scop_snip(
  df_scop_snip,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)
```

##### **Journal impact, fractionalized (3-year moving average)** {.mobile}

```{r}
abm_ui_kable_scop_snip(df_scop_snip)
```

##### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.html#scopus){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis"}
cat("<hr>")
cat("This table is based on Scopus publication types Article, Review and Conference Paper.<br>")

if(isTRUE(unit_level >= 0)){

  scopcov_snip <- df_coverage %>%
    filter(Publication_Type == "Peer reviewed", Publication_Year %in% df_scop_snip$Publication_Year)

  mincov <- min(scopcov_snip$scopcov_frac)
  minpubs <- min(scopcov_snip$sumscop_full)
  
  cat(glue("<span title='Legend: 75% or above is good, 60% or above is moderate while lower than 60% is poor'>Rows are based on at least <b>{minpubs}</b> (full counted) publications with ",
           "<b>{coveragetext(mincov)}</b> Scopus coverage (at least <b>{round(100*mincov, 1)}%</b>).<br>",
           "(DiVA publication types Article, peer review and Conference paper, peer review)<br></span>"))

  if(minpubs < 50)
    cat("<b>Indicators based on < 50 publications are considered unreliable</b>")

} else {

  cat("<b>Bibliometric results for individual researchers should always be interpreted with caution.</b>")

}
cat("<hr>")
```
</div>

### Co&#8209;publishing

<div style='display:flex; flex-direction:column; justify-content:space-evenly; align-items:center;'>

##### **International and corporate co&#8209;publication**

```{r, fig.height=4, fig.width = 9}
if(df_scop_copub %>% filter(!is.na(P_full)) %>% nrow() > 0) {
  abm_graph_scop_copub(df_scop_copub)
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```
</div>

##### **International and corporate co&#8209;publications (full counts)** {.no-mobile}

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>

```{r, fig.height = 4}
abm_ui_datatable_scop_copub(
  df_scop_copub,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)
```

##### **International and corporate co&#8209;publications (full counts)** {.mobile}

```{r}
abm_ui_kable_scop_copub(df_scop_copub)
```

##### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.html#scopus){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis"}
cat("<hr>")
cat("This table is based on Scopus publication types Article, Review and Conference Paper.<br>")

if(isTRUE(unit_level >= 0)){
  scopcov_copub <- df_coverage %>%
    filter(Publication_Type == "Peer reviewed", Publication_Year %in% df_scop_copub$Publication_Year)

  mincov <- min(scopcov_copub$scopcov_full)
  minpubs <- min(df_scop_copub$P_full)

  cat(glue("<span title='Legend: 75% or above is good, 60% or above is moderate while lower than 60% is poor'>Rows are based on at least <b>{minpubs}</b> (full counted) publications with ",
           "<b>{coveragetext(mincov)}</b> Scopus coverage (at least <b>{round(100*mincov, 1)}%</b>).<br>",
           "(DiVA publication types Article, peer review and Conference paper, peer review)<br></span>"))

  if(minpubs < 50)
    cat("<b>Indicators based on < 50 publications are considered unreliable</b>")

} else {

  cat("<b>Bibliometric results for individual researchers should always be interpreted with caution.</b>")

}
cat("<hr>")
```



SDG
=====================================

#### `r unit_label`

Row {data-height=650}
---------------------

### **Sustainable Development Goals (fractional counts)**

```{r, fig.height=8, fig.width = 20}
if(df_sdg_table %>% filter(SDG_Displayname != 'None') %>% nrow() > 0) {
  abm_graph_sdg(df_sdg_table)
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```

Row {data-height=800}
---------------------

### **Publications with any Sustainable Development Goal (fractional counts)** {.no-mobile}

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>

```{r, fig.height = 4}
abm_ui_datatable_sdg_year(
  df_sdg_year,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)
```

### **Publications with any Sustainable Development Goal (fractional counts)** {.mobile}

```{r}
abm_ui_kable_sdg_year(df_sdg_year)
```


### **Sustainable Development Goals (fractional counts)** {.no-mobile}

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>

```{r, fig.height = 4}
abm_ui_datatable_sdg_table(
  df_sdg_table,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)
```

### **Sustainable Development Goals (fractional counts)** {.mobile}

```{r}
abm_ui_kable_sdg_table(df_sdg_table)
```

Row
---------------------

### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.html#sdg){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis"}
cat("This table is based on Scopus publication types Article, Review and Conference Paper.<br>")

if(isTRUE(unit_level >= 0)){

  years <- df_scop_cit %>% filter(substr(Publication_Year_ch, 1, 1) == "2") %>% pull(Publication_Year_ch) %>% as.integer()
  mincov <- df_coverage %>% filter(Publication_Type == "Peer reviewed" & Publication_Year %in% years) %>% pull(scopcov_frac) %>% min()
  minpubs <- df_coverage %>% filter(Publication_Type == "Peer reviewed" & Publication_Year %in% years) %>% pull(sumscop_full) %>% min()

  cat(glue("<span title='Legend: 75% or above is good, 60% or above is moderate while lower than 60% is poor'>Rows are based on at least <b>{minpubs}</b> (full counted) publications with ",
           "<b>{coveragetext(mincov)}</b> Scopus coverage (at least <b>{round(100*mincov, 1)}%</b>).<br>",
           "(DiVA publication types Article, peer review and Conference paper, peer review)<br></span>"))

} else {

  cat("<b>Bibliometric results for individual researchers should always be interpreted with caution.</b>")

}
```

### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.html#sdg){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis"}
cat("This table is based on Scopus publication types Article, Review and Conference Paper.<br>")

if(isTRUE(unit_level >= 0)){

  years <- df_scop_cit %>% filter(substr(Publication_Year_ch, 1, 1) == "2") %>% pull(Publication_Year_ch) %>% as.integer()
  mincov <- df_coverage %>% filter(Publication_Type == "Peer reviewed" & Publication_Year %in% years) %>% pull(scopcov_frac) %>% min()
  minpubs <- df_coverage %>% filter(Publication_Type == "Peer reviewed" & Publication_Year %in% years) %>% pull(sumscop_full) %>% min()

  cat(glue("<span title='Legend: 75% or above is good, 60% or above is moderate while lower than 60% is poor'>Rows are based on at least <b>{minpubs}</b> (full counted) publications with ",
           "<b>{coveragetext(mincov)}</b> Scopus coverage (at least <b>{round(100*mincov, 1)}%</b>).<br>",
           "(DiVA publication types Article, peer review and Conference paper, peer review)<br></span>"))

} else {

  cat("<b>Bibliometric results for individual researchers should always be interpreted with caution.</b>")

}
```

<i class="fa fa-info-circle" aria-hidden="true"></i> About
===========================

#### 

Row  {data-height=1024}
---------------------

<iframe allowfullscreen="true" src="https://KTH-Library.github.io/abm/About_ABM.html" style="border: 0px solid #ddd; min-height: 1024px" width="100%" height="100%" data-external="1"></iframe>
