---
title: "ABM"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    favicon: kth-logo.png
    fig_mobile: FALSE
params:
  unit_code: !r bibliomatrix:::abm_config()$default_unit
  is_employee: FALSE
  use_package_data: TRUE
  embed_data: FALSE
---

```{r setup, include=FALSE}
# unit_codes for testing:

# u1g9umtq
# u1jr9fll 
# u1ygqmuy
# u13bp6vd
# u18qe64m   <- NB: this one triggers an exception in sliding_intervals() fcn

library(flexdashboard)
library(DT)
library(readr)
library(purrr)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(bibliomatrix)
library(tidyr)
library(scales)
library(plotly)
library(kableExtra)

colors_vb <- palette_kth(4)

# Retrieve result tables to use in tabs and key indicators

if (params$use_package_data != TRUE) {
  con <- pool_bib()
  df_diva <- abm_table1(con = con, unit_code = params$unit_code) 
  df_cit3y <- abm_table2(con = con, unit_code= params$unit_code)
  df_cf <- abm_table3(con = con, unit_code= params$unit_code)
  df_jcf <- abm_table4(con = con, unit_code= params$unit_code)
  df_copub <- abm_table5(con = con, unit_code= params$unit_code)
  unit_meta <- unit_info(con = con) %>% filter(unit_code == params$unit_code)
  pool::poolClose(con)
} else {
  df_diva <- pluck(abm_public_kth$units, params$unit_code, 1)
  df_cit3y <- pluck(abm_public_kth$units, params$unit_code, 2)
  df_cf <- pluck(abm_public_kth$units, params$unit_code, 3)
  df_jcf <- pluck(abm_public_kth$units, params$unit_code, 4)
  df_copub <- pluck(abm_public_kth$units, params$unit_code, 5)
  unit_meta <- filter(abm_public_kth$meta, unit_code == params$unit_code)
}

if (params$is_employee) {
  
  unit_label <- 
    ad_displayname(kthid = params$unit_code)
  
} else {
  
  unit_label <- 
    abm_public_kth$meta %>% 
    filter(unit_code == params$unit_code) %>%
    pull(unit_long_en)
}

```


Overview
===========================

#### `r unit_label`

Row  {data-height=240}
---------------------

```{r}
yrfields <- grep("^[1-2][0-9]{3}$", names(df_diva))
firstyear <- min(names(df_diva[yrfields]))
lastyear <- max(names(df_diva[yrfields]))
```

### **Publications in DiVA `r lastyear`<br>(fractional counts)**

```{r, fig.width = 3, fig.height = 2}
if (nrow(df_diva) > 0) {
  
  total_pubs <- sum(df_diva[, lastyear], na.rm = TRUE)
  
  vb1 <- valueBox(
    value = round(total_pubs, 1),
    color = colors_vb[1],
    icon = "fa-chart-bar",
    href = "#publications-in-diva")
  
  vb1
}

```

### **WoS coverage `r firstyear` - `r lastyear`<br>(peer reviewed)**

```{r, fig.width = 3, fig.height = 2}
if (nrow(df_diva) > 0) {
  
  totcov <- df_diva %>% filter(Publication_Type_DiVA %in% 
      c("Article, peer review", "Conference paper, peer review")) %>% 
    summarise(totcov = sum(P_frac * WoS_coverage) / sum(P_frac)) %>% 
    pull(totcov)
  
  vb2 <- valueBox(
    value = paste(100*round(totcov, 3), "%"),
    color = colors_vb[1],
    icon = "fa-percent",
    href = "#publications-in-diva")
  
  vb2
}

```
```{r}
has_rows <- df_cf %>% filter(!is.na(P_frac)) %>% nrow() > 0
last_interval <- ifelse(has_rows, nth(df_cf$interval, -2), "")

```

### **[Citation impact `r last_interval`](#citation-impact)** {.no-padding .no-mobile}

```{r, fig.width = 3.5, fig.height = 2}
library(patchwork)

if (has_rows == TRUE) {
  
  cf <- df_cf %>% filter(interval == last_interval) %>% pull(cf) %>% as.numeric()
  
  pub_bullet1 <- abm_bullet(label = "Field normalized citations (Cf)", 
    value = cf, reference = 1.0, roundto = 2)
  
  top10_share <- as.numeric(filter(df_cf, interval == last_interval)$top10_share)
  
  pub_bullet2 <- abm_bullet(label = "Share Top10% publications", 
    value = top10_share, reference = 0.10, pct = TRUE)
  
  #bullets <- grid.arrange(pub_bullet1, pub_bullet2, ncol = 1)
  
  bullets <- pub_bullet1 / pub_bullet2
  
  bullets
}

```

### **[Citation impact `r last_interval`](#citation-impact)** {.no-padding .mobile}

```{r, fig.width=3.75, fig.height = 2}
bullets
```

```{r}

has_rows <- df_jcf %>% filter(!is.na(P_frac)) %>% nrow() > 0
last_interval <- ifelse(has_rows, nth(df_jcf$interval, -2), "")

```
### **[Journal impact `r last_interval`](#journal-impact)**  {.no-padding .no-mobile}

```{r, fig.width=3.75, fig.height = 2} 
if (has_rows == TRUE) {
  
  jcf <- df_jcf %>% filter(interval == last_interval) %>% pull(jcf) %>% as.numeric()
  
  jour_bullet1 <- abm_bullet(label = "Field normalized journal citations (JCf)", 
    value = jcf, reference = 1.0, roundto = 2)

  top20_share <- as.numeric(filter(df_jcf, interval == last_interval)$top20_share)
  
  jour_bullet2 <- abm_bullet(label = "Share in Top20% journals", value = top20_share, 
    reference = 0.20, pct = TRUE)
  
  bullets <- jour_bullet1 / jour_bullet2
  
  bullets
}

```

### **[Journal impact `r last_interval`](#journal-impact)**  {.no-padding .mobile}

```{r, fig.width=3.75, fig.height = 2}
bullets
```


```{r}
has_rows <- df_copub %>% filter(!is.na(P_full)) %>% nrow > 0
last_interval <- nth(df_copub$interval, -2)
```

### **[Co-publishing `r last_interval`](#co-publishing)** {.no-padding .no-mobile}
```{r, fig.width = 3.75, fig.height = 2.5}

if (has_rows) {
  
  nonuniv_share <- as.numeric(filter(df_copub, interval == last_interval)$nonuniv_share)
  nonuniv_lbl <- sprintf("Swedish non-university: %d%%", round(100 * nonuniv_share))
  waffle1 <- abm_waffle_pct(nonuniv_share, label = nonuniv_lbl) 

  int_share <- as.numeric(filter(df_copub, interval == last_interval)$int_share)
  int_lbl <- sprintf("International: %d%%", round(100*int_share))
  waffle2 <- abm_waffle_pct(int_share, label = int_lbl)

  waffles <- waffle1 / waffle2
  
  waffles
}
```

### **[Co-publishing `r last_interval`](#co-publishing)** {.no-padding .mobile}

```{r, fig.width = 3.75, fig.height = 2.5}
waffles
```

Row
--------------------------------

### **Background**

The bibliometric indicators referred are based on publications registered in DiVA and published 2012 to 2018. Only publications which have been affiliated to KTH are included. This means that publications written by a researcher before she/he was employed at KTH, and that are not affiliated to KTH, will not be included in the statistics.

Statistics regarding citations and co-publishing are based on the subset of publications in DiVA that are registered in Web of Science.

### **Further information**

```{r}
# TODO: change to suitable location for static PDF assets (or other non-HTML resources)
STATIC <- "https://kth-library.github.io/abm"
```

- [Guide to the Annual Bibliometric Monitoring at KTH](`r STATIC`/ABM_guide.pdf){target="_blank"}
- [Description of data, methods and indicators in KTH Annual Bibliometric Monitoring](`r STATIC`/Description_data_and_methods_ABM.pdf){target="_blank"}
- [Formal definitions of field normalized citation indicators at KTH](`r STATIC`/Formal_definitions_field_normalized_citation.pdf){target="_blank"}
- [Information about DiVA and the registration process - Handle publications in DiVA](https://www.kth.se/en/biblioteket/publicera-analysera/hantera-publikationer){target="_blank"}
- [President decision about the Annual Bibliometric Monitoring](`r STATIC`/Beslut_ABM.pdf){target="_blank"}

Row
----------------------

### **Publication data**

```{r, echo=FALSE, results="asis"}

if (params$embed_data == TRUE) {
  
  library(htmltools)
  
  embed_data <- function(path)
    paste0("data:", mime::guess_type(path), ";base64,", 
      base64enc::base64encode(path))
  
  embed_file_link <- function(path,
    href = embed_data(path),
    name = basename(path),
    text = paste("Download", name), ...) {
    withTags(p(a(text, href = href, download = name, ...)))
  }
  
  icon_download <- htmltools::tag("i", list(
    class = "fa fa-download", 
    paste("Publication data for", unit_label)))
  
  icon_download <- htmltools::attachDependencies(icon_download,
    flexdashboard:::html_dependencies_fonts(TRUE, FALSE))
  
  # export to xlsx format, into tempdir so we can embed a file link
  
  # data that we want to export
  con <- pool_bib()
  publications_kth <- abm_publications(con = con, unit_code = params$unit_code)
  pool::poolClose(con)
  
  #install.packages("openxlsx")
  library(openxlsx)
  excel_file <- file.path(tempdir(), "PublList_KTH.xlsx")
  write.xlsx(publications_kth, excel_file)
  
  embed_file_link(excel_file,
    title = "Download Publication List in Excel format",
    text = icon_download, 
    class = "btn btn-sm btn-primary")
}
```


```{r, echo=FALSE, results="asis"}

if (params$embed_data == TRUE && params$is_employee == TRUE) {
  out <- '<a href="https://kth.diva-portal.org/dream" class="btn btn-sm btn-primary">Edit your publication data in DiVA</a><p>Please register publications in DiVA as soon as possible for these to be included in the Annual Bibliometric Monitoring.</p>'
  cat(out)
} else {
  cat("Publication data is available only after login.")
}
  
```

### **Attributions**

```{r, echo=FALSE, message=FALSE, results="asis"}
wos_disclaimer()
```

Publications in DiVA
=====================================

#### `r unit_label`

Row
---------------------

### **Publication volume, fractionalized** {.no-padding .no-mobile}

<!-- <div style='width:720px;margin:auto'> -->

```{r, fig.width=3.75}
if (nrow(df_diva) > 0) {
  
  df <- df_diva %>% rename(
    "WoS coverage" = "WoS_coverage",
    "DiVA publication type" = "Publication_Type_DiVA",
    "Total" = "P_frac")
  
  dt <- 
    DT::datatable(df,
      rownames = FALSE,
      extensions = c("Buttons"), #c("Buttons", "Scroller"), 
      style = "bootstrap", class = "compact", width = "720",
      options = list(
        #deferRender = TRUE, scroller = TRUE, scrollX = TRUE,
        ordering = FALSE,
        bPaginate = FALSE,
        pageLength = 100,
        dom = 'Bt',
        buttons = list("copy", "csv", "excel"),
        title = "ABM_publications")
      ) %>%
    formatRound(2:9, digits = 1, mark = "") %>%
    formatPercentage("WoS coverage", digits = 1) %>%
    abm_format_rows()
  
  dt
}

```
<!-- </div> -->

### **Publication volume, fractionalized** {.no-padding .mobile}

```{r, fig.width=3.75}

df %>% 
  mutate_at(vars(starts_with("201"), starts_with("Total")), round, digits = 1) %>%
  mutate_at(vars(starts_with("WoS")), function(x) sprintf("%3.1f%%", x * 100)) %>%
  kable() %>% 
  kable_styling(bootstrap_options = c("responsive")) %>%
  scroll_box(width = "720px")
```


Row
---------------------

### **Publication volume** {.no-padding .no-mobile}

```{r, fig.width=10, fig.height=10}
if (nrow(df_diva) > 0) {
  p <- abm_graph_diva(df_diva)
  p
}
```

### **Publication volume** {.no-padding .mobile}

```{r, fig.width=10, fig.height = 9.6, out.width=3.75}
p
#library(magick)
# 3.75 x 4.8
#ggsave("/tmp/plot.png", p, width = 3.75 * 2, height = 4.8 * 2)
#image_read("/tmp/plot.png") %>% image_trim() %>% image_resize("360x460")
```

### **Web of Science coverage** {.no-padding .no-mobile}

```{r, fig.width=7, fig.height=8}
if (nrow(df_diva) > 0) {
  p <- abm_graph_wos_coverage(df_diva)
  p
}
```

### **Web of Science coverage** {.no-padding .mobile}

```{r, fig.width=9, fig.height=6}
p
```


Citation impact
=====================================

#### `r unit_label`

Row
---------------------

### **Citations 3-year window, fractional counts** {.no-mobile}

```{r}
df <- df_cit3y %>% rename(
  "Publication year" = "Publication_Year_ch",
  "Publications" = "P_frac",
  "Total Citations" = "C3_frac",
  "Average Citations" = "C3"
) %>% select("Publication year", "Publications", "Total Citations", "Average Citations")

if (nrow(df) > 0)
  DT::datatable(df,
    rownames = FALSE,
    extensions = "Buttons",
    options = list(
      bPaginate = FALSE,
      dom = 'Bt',
      buttons = c("copy", "csv", "excel"),
      title = "ABM_citations")
    ) %>% 
    formatRound(2:4, digits = 1, mark = "") %>%
    abm_format_rows()
```

### **Citations 3-year window, fractional counts** {.mobile}

```{r}

df %>% 
  mutate_at(vars(2:4), function(x) sprintf("%.1f", x)) %>%
  kable() %>% 
  kable_styling(bootstrap_options = c("responsive")) %>%
  scroll_box(width = "720px")

```

### **Field normalized citations - Fractionalized (3-year moving average)** {.no-mobile}

```{r} 
df <- df_cf %>% rename(
  "Publication years" = "interval",
  "Publications" = "P_frac",
  "Average Cf" = "cf",
  "Top 10% publications" = "top10_count",
  "Share Top 10%" = "top10_share")

if (nrow(df) > 0) {
  DT::datatable(df,
    rownames = FALSE,
    extensions = "Buttons",
    options = list(
      bPaginate = FALSE,
      dom = 'Bt',
      buttons = c("copy", "csv", "excel"),
      filename = "ABM_field_normalized_citations")
    ) %>% 
    formatRound(c(2, 4), digits = 1, mark = "") %>% 
    formatRound(3, digits = 2, mark = "") %>%
    formatPercentage(5, digits = 1) %>%
    abm_format_rows()
}
```

### **Field normalized citations - Fractionalized (3-year moving average)** {.no-padding .mobile}

```{r}
df %>% 
  mutate_at(vars(2, 4), function(x) sprintf("%.1f", x)) %>%
  mutate_at(vars(3), function(x) sprintf("%.2f", x)) %>%
  mutate_at(vars(5), function(x) sprintf("%.1f%%", x * 100)) %>%
  kable() %>% 
  kable_styling(bootstrap_options = c("responsive")) %>%
  scroll_box(width = "720px")
```


Row
---------------------

### **Average field normalized citations (Cf)**

```{r}
if (df_cf %>% filter(!is.na(P_frac)) %>% nrow > 0)
  abm_graph_cf(df_cf)
```


### **Share Top 10%**

```{r}
if (df_cf %>% filter(!is.na(P_frac)) %>% nrow > 0)
  abm_graph_top10(df_cf)
```


Journal impact
=====================================

#### `r unit_label`

Row
---------------------

### **3-year moving average, fractional counts** {.no-mobile}

```{r}
df <- df_jcf %>% rename(
  "Publication years" = "interval",
  "Publications" = "P_frac",
  "Average Journal Cf" = "jcf",
  "Publications in Top 20% journals" = "top20_count",
  "Share Top 20% journals" = "top20_share"
)

if (nrow(df) > 0)
  DT::datatable(df,
    rownames = FALSE,
    extensions = "Buttons",
    options = list(
      bPaginate = FALSE,
      dom = 'Bt',
      buttons = c("copy", "csv", "excel"),
      title = "ABM_journal_impact")
    ) %>% 
    formatRound(c(2, 4), digits = 1, mark = "") %>% 
    formatRound(3, digits = 2, mark = "") %>% 
    formatPercentage(5, digits = 1) %>%
    abm_format_rows()
```

### **3-year moving average, fractional counts** {.no-padding .mobile}

```{r, fig.width=3.75}
df %>% 
  mutate_at(vars(2, 4), function(x) sprintf("%.1f", x)) %>%
  mutate_at(vars(3), function(x) sprintf("%.2f", x)) %>%
  mutate_at(vars(5), function(x) sprintf("%.1f%%", x * 100)) %>%
  kable() %>% 
  kable_styling(bootstrap_options = c("responsive")) %>%
  scroll_box(width = "720px")
```



Row
---------------------

### **Field normalized journal indicator (JCf)**

```{r}
if(df_jcf %>% filter(!is.na(P_frac)) %>% nrow > 0)
  abm_graph_jcf(df_jcf)
```


### **Share Journal Top 20%**

```{r}
if(df_cf %>% filter(!is.na(P_frac)) %>% nrow > 0)
  abm_graph_top20(df_jcf)
```

Co-publishing
=====================================

#### `r unit_label`

Row
---------------------

### **International and Swedish non-university co-publications (full counts)** {.no-mobile}

```{r}
df <- df_copub %>% rename(
  "Publication years" = "interval",
  "Publications" = "P_full",
  "Swedish non-university co-publications" = "nonuniv_count",
  "Share Swedish non-university" = "nonuniv_share",
  "International co-publications" = "int_count",
  "Share international" = "int_share")

if (nrow(df) > 0) {
  DT::datatable(df,
    rownames = FALSE,
    extensions = "Buttons",
    options = list(
      bPaginate = FALSE,
      dom = 'Bt',
      buttons = c("copy", "csv", "excel"),
      title = "ABM_co-publications")
    ) %>%
    formatPercentage(c(4,6), digits = 1) %>%
    abm_format_rows()
}
```

### **International and Swedish non-university co-publications (full counts)** {.no-padding .mobile}

```{r, fig.width=3.75}
df %>% 
  mutate_at(vars(4, 6), function(x) sprintf("%.1f%%", x * 100)) %>%
  kable() %>% 
  kable_styling(bootstrap_options = c("responsive")) %>%
  scroll_box(width = "720px")
```


Row
-------

### **International and Swedish non-university co-publication**

```{r, fig.width=6, fig.height=4}
if(df_copub %>% filter(!is.na(P_full)) %>% nrow > 0)
  abm_graph_copub(df_copub)

```
