---
title: "KTH Divisions in ABM"
output: 
  flexdashboard::flex_dashboard:
    logo: beta-logo.png
    favicon: kth-logo.png
    orientation: rows
    vertical_layout: fill
params:
  snakify: TRUE
  baseurl: "/ui/divisions/"
---

```{r, results='asis'}
cat(sprintf("<style>                     
.navbar {
  background-color:%s;
}
</style>", unname(bibliomatrix::palette_kth()["cerise"])
))                  

```

<!--
Divisions {.tabset .tabset-fade}
-------------------------------------

### Divisions
--->

# Overview

### Divisions overview

Divisions with links lead to a more detailed report and appear if the unit has more more than 4 distinct researchers with DiVA publications referenced in Web Of Science. Tooltips provide explanation for the table headings (on hover).

```{r}
library(bibliomatrix)
library(dplyr)
library(DT)
library(formattable)

linkify <- function(x, y)
  sprintf("<a href='%s' target='_blank'>%s</a>", paste0(params$baseurl, sapply(y, function(z) URLencode(z, reserved = TRUE))), x)

snakify <- function(x) gsub("/", "_", x, fixed = TRUE)

if (params$snakify == TRUE)
  linkify <- function(x, y)
      sprintf("<a href='%s' target='_blank'>%s</a>", paste0(params$baseurl, sapply(y, function(z) snakify(z))), x)

ds <- 
  con_bib("sqlite") %>% tbl("division_stats") %>% 
  collect() %>% 
  arrange(nd_researchers, n_pubs) %>% 
  select(starts_with("n"), everything()) %>%
  select(-c("pid", "desc_parent")) %>%
  select(id = id, desc, everything()) %>%
  mutate(has_link = (n_pubs > 0 & (nd_researchers > 4))) %>%
  mutate(q1 = round(100 * nd_researchers / n_staff, 1)) %>%
  mutate(q2 = round(100 * n_pubs_wos / n_pubs, 1)) %>%
  mutate(desc = ifelse(has_link, linkify(desc, id), desc)) %>%
  arrange(desc(q2)) %>%
  select(Slug = id, `Divison`=desc, n_staff, nd_researchers, q1, n_pubs, n_pubs_wos, q2)

  color_tile_divergent <- function(x) ifelse(x <= 0, 
    color_tile("lightpink", "transparent")(x * c(x <= 0)),
    color_tile("transparent", "lightblue")(x * c(x > 0)))

  headers <- c(colnames(ds))

  lookup <- readr::read_csv("field,tooltip
  Slug,Organizational slug or short code
  Division,Organizational name from KTH Catalogue
  n_staff,Number of staff at the organizational unit
  nd_researchers,Number of staff with publications in DiVA during the period
  q1,Ratio between staff with publications and total staff at the unit
  n_pubs,Number of publications in DiVA during the period
  n_pubs_wos,Number of publications covered in Web Of Science
  q2,Ratio between publications in Web Of Science and those in DiVA")

  tooltip <- function(x) {
    lookup %>% left_join(tibble(tooltip = x)) %>% pull(tooltip)
  }
   
  library(htmltools)

  header_style <- function(x) paste(collapse = ",", sprintf(paste0(
    "th('%s', class = 'display dt-left', style = ", 
    "'padding-left: 10px; padding-right: 10px;', title = '%s')"), 
      x, tooltip(x)))

  tt <- header_style(headers)
  my_container <- eval(parse(text = paste0(
    "withTags(table(class = 'display dt-right', thead(tr(list(", tt , ")))))")))

fdt <- function(data)
  as.datatable(rownames = FALSE, class = "stripe", 
    container = my_container, 
    options = list(
      initComplete = htmlwidgets::JS("
          function(settings, json) {
            $(this.api().table().container()).css({
            'font-size': '12px',
            });
          }
      "),
      columnDefs = list(list(className = 'dt-left', targets = "_all")),
      pageLength = 300L, bPaginate = FALSE, scrollY = 380,
      dom = 'ftB'), x = formattable(data, 
        align = c("l", "l", rep("r", length(headers) - 2)),
        list(
          n_staff = color_bar("lightgray"),
          nd_researchers = color_bar("lightgray"),
          n_pubs = color_bar("lightblue"),
          n_pubs_wos = color_bar("lightblue"),
          q1 = color_tile("transparent", unname(palette_kth()["olive"])),
          q2 = color_tile("transparent", unname(palette_kth()["olive"]))
        )
    )) %>% 
  DT::formatStyle(columns = colnames(.$x$data), 
      `font-size` = "12px", 
      `class` = "display dt-right",
      `style` = "padding-left: 10px"
      )

fdt(ds)
```

# Explore graph

### Explore divisions graph

Data from KTH Directory API. Click a node for details (opens KTH website), scroll to zoom, drag to pan. Nodes can be dragged around.

```{r, out.width="100%"}
le <- function(x) URLencode(x, reserved = TRUE)

exclude <- 
  ds %>% mutate(has_link = (n_pubs > 0 & (nd_researchers > 4))) %>% 
  filter(has_link == FALSE) %>% pull(Slug)

exclude <- c(exclude, "KTH")

if (params$snakify == TRUE)
  le <- snakify

fn <- abm_graph_divisions(
  base_url = params$baseurl, 
  link_encoder = le,
  links_exclude = exclude,
  use_size = TRUE,
  prune_graph = TRUE
) 

fn$width <- "80%"
fn$height <- "80%"

#fn
#htmlwidgets::saveWidget(fn, "~/abm-divisions.html")
#browseURL("~/abm-divisions.html")

fn <- htmlwidgets::onRender(
  fn,
  '
function(el,x){
debugger;
  var optArray = [];
  for (var i = 0; i < x.nodes.name.length - 1; i++) {
    optArray.push(x.nodes.name[i]);
  }

  optArray = optArray.sort();

  $(function () {
    $("#search").autocomplete({
      source: optArray
    });
  });

  d3.select(".ui-widget button").node().onclick=searchNode;

  function searchNode() {
    debugger;
    //find the node

    var selectedVal = document.getElementById("search").value;
    var svg = d3.select(el).select("svg");
    var node = d3.select(el).selectAll(".node");

    if (selectedVal == "none") {
      node.style("stroke", "white").style("stroke-width", "10");
    } else {
      var selected = node.filter(function (d, i) {
        return d.name != selectedVal;
      });
      selected.style("opacity", "0");
      var link = svg.selectAll(".link")
      link.style("opacity", "0");
      d3.selectAll(".node, .link").transition()
        .duration(5000)
        .style("opacity", 1);
    }
  }
}  
  '
)
library(htmltools)

browsable(
  attachDependencies(
    tagList(
      tags$head(
        tags$link(
          href="https://code.jquery.com/ui/1.11.0/themes/smoothness/jquery-ui.css",
          rel="stylesheet"
        )
      ),
      HTML(
        '
  <div class="ui-widget" style="display: flex; justify-content: flex-end">
      <input id="search">
      <button type="button">Search</button>
  </div>
  '     
      ),
      fn
    ),
    list(
      rmarkdown::html_dependency_jquery(),
      rmarkdown::html_dependency_jqueryui()
    )
  )
)

```



 ```{r subpages, include=FALSE}

#d <- ds %>% slice(1:5)

# d <- data.frame(id = c("c", "s"), desc = c("chem", "phys"))
# 
# out <- NULL

# allow duplicate labels (needed for subpages)
# options(knitr.duplicate.label = "allow")
# 
# subpage_env <- new.env()


# for (i in seq_along(d$id)) {
# 
#   assign("subpage_data", d[i,]$id, subpage_env)
#   assign("division", d[i,]$desc, subpage_env)
#   
#   out <- c(out, knitr::knit_child("subpage.Rmd", envir = subpage_env))
# 
# }

```

<!-- `r #paste(knitr::knit_child(text = out), collapse = "")` -->

# Information {data-orientation=rows data-icon="fa-info-circle"}

### Author-based Annual Bibliometric Monitoring report

**Data sources:**

- Publications listed in DiVA in the period `r abm_config()$start_year`-`r abm_config()$stop_year` for `r abm_config()$default_unit` are included.

- Staff data comes from the KTH Catalogue API, which lists employees current organizational belonging in KTH.

**Data scope:**

Some units are large, while other divisions can be quite small. Units where more than *4 currently employed* researchers that have made contributions during the period are listed with a link to a more detailed report for that specific division. 
Smaller units with few publications do not provide such a link. This is done in order to avoid exposing individual researcher data, and to display results for that are big enough to allow meaningful calculations of bibliometric indicators.

### Difference from "regular" ABM report

- An overview is provided for Divisions, with some aggregate data at unit level
- Only publications from **currently employed staff** are included
- Results can be strongly influenced by staff turnover

Please email your questions or ideas for improvements to [biblioteket@kth.se](mailto:biblioteket@kth.se)

