---
title: "Rolling ABM"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    logo: beta-logo.png
    favicon: kth-logo.png
    fig_mobile: FALSE
params:
  unit_code: "a"
  is_employee: FALSE
  use_package_data: TRUE
  embed_data: TRUE
---

```{r setup, include=FALSE}
library(flexdashboard)
library(DT)
library(readr)
library(purrr)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(bibliomatrix)
library(tidyr)
library(scales)
#library(plotly)
library(kableExtra)
library(glue)
library(extrafont)

colors_vb <- palette_kth(4)

# Retrieve result tables to use in tabs and key indicators

# Get authorbased data for selected org
unit_code <- params$unit_code
con <- con_bib()
unit_members <- abm_researchers(unit_code)
unit_publ<- abm_staff_data(con, unit_members)
df_copub_countries <- abm_copub_countries_staffbased(con = con,
                                                     publist = unit_publ)
df_copub_orgs <- abm_copub_orgs_staffbased(con = con,
                                           publist = unit_publ)
df_sdg_year <- abm_sdg_year(con = con,
                            data = unit_publ)
df_sdg_table <- abm_sdg_table(con = con,
                              data = unit_publ)
DBI::dbDisconnect(con)

# Get ABM tables
df_diva <- abm_table1(unit_publ)
df_diva_full <- abm_table1_full(unit_publ)
df_cit3y <- abm_table2(unit_publ)
df_cf <- abm_table3(unit_publ)
df_jcf <- abm_table4(unit_publ)
df_copub <- abm_table5(unit_publ)
df_oa <- abm_table6(unit_publ)
df_scop_cit <- abm_table_scop_cit(unit_publ)
df_scop_normcit <- abm_table_scop_normcit(unit_publ)
df_scop_snip <- abm_table_scop_snip(unit_publ)
df_scop_copub <- abm_table_scop_copub(unit_publ)
df_coverage <- abm_coverage(unit_publ)

unit_level<- 2

if (unit_code %in% unit_info()$slug) {
  unit_label <- unit_info() %>% filter(slug == params$unit_code) %>% pull(unit_long_en)
} else {
  unit_label <- abm_divisions() %>% filter(id == unit_code) %>% pull(desc)
}

unit_file_label<- gsub("/", "_", unit_code)
current_date <- format(Sys.Date(), "%Y%m%d")
abm_unit_title<- paste0("ABM: ",unit_label)

# TODO: change to suitable location for static PDF assets (or other non-HTML resources)
STATIC <- "https://kth-library.github.io/abm"

```

```{r, results='asis'}
cat(sprintf("<style>                     
.navbar {
  background-color:%s;
}
.nav-tabs-custom > .nav-tabs > li > a {
  font-size: 1.5rem
}
</style>", unname(bibliomatrix::palette_kth()["cerise"])
))                  

```  

Overview
===========================

#### `r unit_label`

Row  {data-height=240}
---------------------

```{r}
yrfields <- grep("^[1-2][0-9]{3}$", names(df_diva), value = TRUE)
firstyear <- min(yrfields)
lastyear <- max(yrfields)
```

### **Publications in DiVA `r ifelse(!is.na(lastyear), lastyear, "")`<br>(fractional counts)**

```{r, fig.width = 1.75, fig.height = 2}
abm_ui_valuebox_publications(df_diva, lastyear, colors_vb["cerise"], unit_label)
```

### **WoS coverage `r ifelse(!is.na(firstyear), paste(firstyear, "-", lastyear), "")`<br>(peer reviewed)**

```{r, fig.width = 1.75, fig.height = 2}
abm_ui_valuebox_coverage(df_coverage, colors_vb["cerise"], "wos", unit_label)
```

### **Scopus coverage `r ifelse(!is.na(firstyear), paste(firstyear, "-", lastyear), "")`<br>(peer reviewed)**

```{r, fig.width = 1.75, fig.height = 2}
abm_ui_valuebox_coverage(df_coverage, unname(palette_kth()["gray"]), "scopus", unit_label)
```


```{r}
has_rows <- df_cf %>% filter(!is.na(P_frac)) %>% nrow() > 0
last_interval <- ifelse(has_rows, nth(df_cf$interval, -2), "")

```

### **[Citation impact `r last_interval` (WoS)](#citation-impact)** {.no-padding .no-mobile}

```{r, fig.width = 3.7, fig.height = 2}
abm_ui_bullet_citations(df_cf)
```

### **[Citation impact `r last_interval` (WoS)](#citation-impact)** {.no-padding .mobile}

```{r, fig.width=3.75, fig.height = 2}
abm_ui_bullet_citations(df_cf)
```

```{r}
has_rows <- df_jcf %>% filter(!is.na(P_frac)) %>% nrow() > 0
last_interval <- ifelse(has_rows, nth(df_jcf$interval, -2), "")
```
### **[Journal impact `r last_interval` (WoS)](#journal-impact)**  {.no-padding .no-mobile}

```{r, fig.width=3.8, fig.height = 2} 
abm_ui_bullet_journal(df_jcf)
```

### **[Journal impact `r last_interval` (WoS)](#journal-impact)**  {.no-padding .mobile}

```{r, fig.width=3.75, fig.height = 2}
abm_ui_bullet_journal(df_jcf)
```


```{r}
has_rows <- df_copub %>% filter(!is.na(P_full)) %>% nrow > 0
last_interval <- ifelse(has_rows, nth(df_copub$interval, -2), "")
```

### **[Co&#8209;publishing `r last_interval` (WoS)](#co&#8209;publishing)** {.no-padding .no-mobile}
```{r, fig.width=3.75, fig.height = 2}
abm_ui_waffle_copub(df_copub)
```

### **[Co&#8209;publishing `r last_interval` (WoS)](#co&#8209;publishing)** {.no-padding .mobile}

```{r, fig.width=2.75, fig.height = 2}
abm_ui_waffle_copub(df_copub)
```

Row
--------------------------------

### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.pdf){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis"}
woscov <- df_coverage %>% 
    filter(Publication_Type == "Peer reviewed") %>% 
    summarise(woscov = sum(sumwos_frac) / sum(p_frac)) %>% 
    pull(woscov)

cat("<p>Indicators in the Citation impact, Journal impact and Co&#8209;publishing tabs are based on Web of Science publications only. Corresponding Scopus indicators can be found under the Scopus tab.</p>")

if(isTRUE(unit_level >= 0) && nrow(df_coverage %>% filter(Publication_Type == "Peer reviewed")) > 0) {

  #<span title='mytitle' onclick=\"window.location.href='https://KTH-Library.github.io/abm/ABM_guide.pdf';\" style='cursor: pointer;></span>'
  glue("<p><span title='Legend: 75% or above is good, 60% or above is moderate while lower than 60% is poor'>Overall Web of Science coverage for peer reviewed publications in this unit is ",
       "{coveragetext(woscov)}, {100*round(woscov, 3)}%.</span></p>")

} else {

  cat("<p><b>Bibliometric results for individual researchers should always be interpreted with caution. </b></br/>
      Bibliometric indicators work best at an aggregated level, and at the individual level 
      the publication profile of researchers, their collaboration networks and their subject specialization may 
      interact with e.g. the field-normalization of citation indicators. The relatively low publication volume of 
      individuals also makes indicator averages very unreliable. </p>")

}

cat("<p>Note that the coverage numbers for Web of Science and Scopus apply to publications in the KTH bibliometric database Bibmet. If a WoS-id or Scoupus-id from DiVA can not be matched in Bibmet, it does not count as covered.</p>")
```

Row
--------------------------------

### **Background**

The bibliometric indicators referred are based on publications registered in DiVA. Only publications from currently employed researchers at KTH are included. The rolling nature of this report means that it provides more of a current overview and less of a historic stable trend, since it excludes publications written by researchers that are no longer affiliated to KTH, but have been at some point in time. 

Indicators in the Citation impact, Journal impact and Co&#8209;publishing tabs are based on Web of Science publications only. Corresponding Scopus indicators can be found under the Scopus tab.

Row
--------------------------------

### **Researchers at the unit**

```{r}
abm_ui_button_publist(
  data = unit_publ,
  is_loggedin = params$embed_data, 
  unit_label = unit_label, 
  unit_code = unit_code, 
  unit_file_label = unit_file_label,
  is_authorbased = TRUE
)
```

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>

```{r}
con <- con_bib()
researchers <- abm_staff_list(con, unit_code)
DBI::dbDisconnect(con)

abm_ui_datatable_researchers(
  data = researchers, 
  unit_file_label = unit_file_label,
  unit_title = abm_unit_title
)
```

Publications in DiVA
=====================================

#### `r unit_label`

Row {.tabset}
---------------------

### Fractional count

#### **Publication volume, fractionalized** {.no-padding .no-mobile}

<!-- <div style='width:720px;margin:auto'> -->

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
table.dataTable thead .sorting_asc, .sorting_desc, .sorting {
    background-image: none !important;
}
</style>

```{r, fig.height=7, fig.width=3.75}

abm_ui_datatable_diva(
  df_diva, 
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)

```
<!-- </div> -->

#### **Publication volume, fractionalized** {.no-padding .mobile}

```{r, fig.width=3.75}
abm_ui_kable_diva(df_diva)
```

### Full count

#### **Publication volume, full count** {.no-padding .no-mobile}

<!-- <div style='width:720px;margin:auto'> -->

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>

```{r, fig.height=7, fig.width=3.75}

abm_ui_datatable_diva_full(
  df_diva_full, 
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)

```
<!-- </div> -->

#### **Publication volume, full count** {.no-padding .mobile}

```{r, fig.width=3.75}
abm_ui_kable_diva_full(df_diva_full)
```


Row
---------------------

### **Publication volume** {.no-padding .no-mobile}

```{r, fig.width=8, fig.height=5}
if (nrow(df_diva) > 0) {
  p <- abm_graph_diva(df_diva)
  p
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```

### **Publication volume** {.no-padding .mobile}

```{r, fig.width=8, fig.height = 5}
if (nrow(df_diva) > 0) {
  p
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
``` 

### **Web of Science coverage by publication type** {.no-padding .no-mobile}

```{r, fig.width=6, fig.height=5}
if (nrow(df_diva %>% left_join(get_pubtype_order(), by = c("Publication_Type_DiVA" = "diva_publication_type")) %>% filter(WoS_coverage != 0)) > 0) {
  p <- abm_graph_wos_coverage(df_diva)
  p
} else {
  shiny::HTML("<p><i>There are no data available for this graph</i></p>")
}
```

### **Web of Science coverage by publication type** {.no-padding .mobile}

```{r, fig.width=6, fig.height=5}
if (nrow(df_diva) > 0) {
  p
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```


Citation impact
=====================================

#### `r unit_label`

Row
---------------------

### **Citations 3-year window, fractional counts** {.no-mobile}

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>
```{r}
abm_ui_datatable_city3y(
  df_cit3y, 
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)
```

### **Citations 3-year window, fractional counts** {.mobile}

```{r}
abm_ui_kable_cit3y(df_cit3y)
```

### **Field normalized citations, fractionalized (3-year moving average)** {.no-mobile}

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>

```{r}
abm_ui_datatable_cf(
  df_cf,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)
```

### **Field normalized citations, fractionalized (3-year moving average)** {.no-padding .mobile}

```{r}
abm_ui_kable_cf(df_cf)
```


Row
--------------------

### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.pdf){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis"}
cat("This table is based on Web of Science publication types Article, Proceedings paper, Review, Letter and Editorial.<br>")

if(isTRUE(unit_level >= 0)){

  years <- df_cit3y %>% filter(substr(Publication_Year_ch, 1, 1) == "2") %>% pull(Publication_Year_ch) %>% as.integer()
  mincov <- df_coverage %>% filter(Publication_Type == "Peer reviewed" & Publication_Year %in% years) %>% pull(woscov_frac) %>% min()
  minpubs <- df_coverage %>% filter(Publication_Type == "Peer reviewed" & Publication_Year %in% years) %>% pull(sumwos_full) %>% min()

  cat(glue("<span title='Legend: 75% or above is good, 60% or above is moderate while lower than 60% is poor'>Rows are based on at least <b>{minpubs}</b> (full counted) publications with ",
           "<b>{coveragetext(mincov)}</b> Web of Science coverage (at least <b>{round(100*mincov, 1)}%</b>).<br>",
           "(DiVA publication types Article, peer review and Conference paper, peer review)<br></span>"))

  if(minpubs < 50)
    cat("<b>Indicators based on < 50 publications are considered unreliable</b>")

} else {

  cat("<b>Bibliometric results for individual researchers should always be interpreted with caution.</b>")

}
```

### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.pdf){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis"}
cat("This table is based on Web of Science publication types Article and Review.<br>")

abm_ui_note(df_cf, df_coverage, unit_level, is_fractional = TRUE)

```

Row
---------------------

### **Average field normalized citations (Cf)**

```{r}
if (df_cf %>% filter(!is.na(P_frac)) %>% nrow() > 0){
  abm_graph_cf(df_cf)
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```


### **Share of publications among Top 10% cited**

```{r}
if (df_cf %>% filter(!is.na(P_frac)) %>% nrow() > 0){
  abm_graph_top10(df_cf)
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```


Journal impact
=====================================

#### `r unit_label`

Row
---------------------

### **Journal impact, fractionalized (3-year moving average)** {.no-mobile}

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>

```{r}
abm_ui_datatable_jcf(
  df_jcf,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)
```

### **Journal impact, fractionalized (3-year moving average)** {.no-padding .mobile}

```{r, fig.width=3.75}
abm_ui_kable_jcf(df_jcf)
```

Row
-----------------

### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.pdf){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis"}
cat("This table is based on Web of Science publication types Article and Review.<br>")

abm_ui_note(df_jcf, df_coverage, unit_level, is_fractional = TRUE)


```

Row
---------------------

### **Field normalized journal impact (JCf)**

```{r}
if(df_jcf %>% filter(!is.na(P_frac)) %>% nrow() > 0) {
  abm_graph_jcf(df_jcf)
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```


### **Share of publications in Top 20% journals**

```{r}
if(df_cf %>% filter(!is.na(P_frac)) %>% nrow() > 0) {
  abm_graph_top20(df_jcf)
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```

Co&#8209;publishing
=====================================

#### `r unit_label`

Row {.tabset}
---------------------

### Summary

#### **International and Swedish non-university co&#8209;publications (full counts)** {.no-mobile}

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>

```{r, fig.height = 14}
abm_ui_datatable_copub(
  df_copub,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)
```

#### **International and Swedish non-university co&#8209;publications (full counts)** {.no-padding .mobile}

```{r, fig.width=3.75}
abm_ui_kable_copub(df_copub)
```

#### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.pdf){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis"}
cat("This table is based on Web of Science publication types Article and Review.<br>")

abm_ui_note(df_copub, df_coverage, unit_level, is_fractional = FALSE, is_wos = TRUE)

```

<div style='display:flex; flex-direction:column; justify-content:space-evenly; align-items:center;'>

#### **International and Swedish non-university co&#8209;publication**
```{r, fig.width=6, fig.height=4}
if(df_copub %>% filter(!is.na(P_full)) %>% nrow() > 0) {
  abm_graph_copub(df_copub)
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```

</div>

### Countries and organizations

#### **Co&#8209;publication countries** {.no-mobile}
<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
table.dataTable thead .sorting_asc, .sorting_desc, .sorting {
    background-image: none !important;
}
</style>
```{r}
abm_ui_datatable_copub_countries(
  df_copub_countries,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
) 
```

#### **Co&#8209;publication countries** {.no-padding .mobile}
```{r}
abm_ui_kable_copub_countries(df_copub_countries) 
```


#### **Co&#8209;publication organizations** {.no-mobile}

```{r}
abm_ui_datatable_copub_orgs(
  df_copub_orgs,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
) 
```

#### **Co&#8209;publication countries** {.no-padding .mobile}
```{r}
abm_ui_kable_copub_orgs(df_copub_orgs) 
```

Open Access
=====================================

#### `r unit_label`

Row
---------------------

### **Open Access publications, full counts** {.no-mobile}
<!-- The DT table headers may have a right alignment issue due to some whitespace issue artifact from disabled sorting? -->
<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
.table th {
  text-align: right;
}
</style>

```{r}
abm_ui_datatable_oa(
  df_oa,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)

```

### **Open Access publications, full counts** {.no-padding .mobile}

```{r, fig.width=3.75}
abm_ui_kable_oa(df_oa)
```


Row
-------

### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.pdf){target="_blank" style="position:relative;float:right;"}

The Open Access type of the publications was fetched from the [Unpaywall REST API](https://unpaywall.org/products/api). The method to determine the OA type is presented [here](https://support.unpaywall.org/support/solutions/articles/44001777288-what-do-the-types-of-oa-status-green-gold-hybrid-and-bronze-mean-).

In summary, the different OA types can be described as follows:

- *Gold:* The full text has been found on a publisher website, in a journal that is fully OA.

- *Hybrid:* The full text has been found on a publisher website, in a journal that is not fully OA.

- *Green:* The full text has been found in an institutional repository, such as DiVA.

- *Bronze:* The full text has been found on a publisher website but no OA license could be identified.


**N.B.**: This table is based on peer-reviewed publications for which Unpaywall could determine the OA type (necessary condition: have a DOI number). Unpaywall's method is empirical and does not strictly equate to copyright license. As a consequence, the OA status of a given publication may vary with time --- for example turning from *"Not OA"* to *"Green"* when a full text is added to DiVA.


Row
-------

### **Overview of Open Access publications - piechart** 

```{r, fig.width=8}
if (df_oa %>% filter(!is.na(P_tot)) %>% nrow() > 0) {
  abm_graph_oadata_piechart(df_oa, type = "ggplot")
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```

### **Stacked area chart for publications**

```{r, fig.width=6}
if (df_oa %>% filter(!is.na(P_tot)) %>% nrow() > 0) {
  abm_graph_oadata_stackedarea(df_oa)
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```

Scopus
=====================================

#### `r unit_label`

Row {.tabset data-height=1200}
-----------------------------------------------------------------------

### Citation Impact

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>

<div style='display:flex; flex-direction:row; justify-content:space-evenly; align-items:center'>

<div>

Column
------

<div style='padding:10px;'>

##### **Citations, open window** {.no-mobile}

```{r, fig.height = 6, fig.width = 6}
abm_ui_datatable_scop_cit(
  df_scop_cit,
  unit_file_label = unit_file_label,
  unit_title = abm_unit_title
)
```

##### **Citations, open window** {.mobile}

```{r}
abm_ui_kable_scop_cit(df_scop_cit)
```

##### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.pdf){target="_blank" style="position:relative; float:right;"}

```{r, echo=FALSE, results="asis"}
cat("<hr>")
cat("This table is based on Scopus publication types Article, Conference Paper, Review, Letter and Editorial.<br>")

if(isTRUE(unit_level >= 0)){

  years <- df_scop_cit %>% filter(substr(Publication_Year_ch, 1, 1) == "2") %>% pull(Publication_Year_ch) %>% as.integer()
  mincov <- df_coverage %>% filter(Publication_Type == "Peer reviewed" & Publication_Year %in% years) %>% pull(scopcov_frac) %>% min()
  minpubs <- df_coverage %>% filter(Publication_Type == "Peer reviewed" & Publication_Year %in% years) %>% pull(sumscop_full) %>% min()

  cat(glue("<span title='Legend: 75% or above is good, 60% or above is moderate while lower than 60% is poor'>Rows are based on at least <b>{minpubs}</b> (full counted) publications with ",
           "<b>{coveragetext(mincov)}</b> Scopus coverage (at least <b>{round(100*mincov, 1)}%</b>).<br>",
           "(DiVA publication types Article, peer review and Conference paper, peer review)<br></span>"))

  if(minpubs < 50)
    cat("<b>Indicators based on < 50 publications are considered unreliable</b>")

} else {

  cat("<b>Bibliometric results for individual researchers should always be interpreted with caution.</b>")

}
cat("<hr>")
```

##### **Average field weighted citation impact (FWCI)**

```{r, fig.height = 4, fig.width = 6}
if(df_scop_normcit %>% filter(!is.na(P_frac)) %>% nrow() > 0) {
  abm_graph_scop_normcit(df_scop_normcit)
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```
</div>
</div>

<div>
<div style='padding:10px;'>

##### **Field weighted citation impact (FWCI)** {.no-mobile}

```{r, fig.height = 6, fig.width = 6}
abm_ui_datatable_scop_normcit(
  df_scop_normcit,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)
```

##### **Field weighted citation impact (FWCI)** {.mobile}

```{r}
abm_ui_kable_scop_normcit(df_scop_normcit)
```

##### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.pdf){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis"}
cat("<hr>")
cat("This table is based on Scopus publication types Article, Review and Conference Paper.<br>")

abm_ui_note(df_scop_normcit, df_coverage, unit_level, is_fractional = TRUE, is_wos = FALSE)

```

##### **Share of publications among Top 10% cited**

```{r, fig.height = 4, fig.width = 6}
if(df_scop_normcit %>% filter(!is.na(P_frac)) %>% nrow() > 0) {
  abm_graph_scop_top10(df_scop_normcit)
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```

</div>
</div>
</div>

### Journal Impact

<div style='display:flex; flex-direction:column; justify-content:space-evenly; align-items:stretch;'>

##### **Journal impact, fractionalized (3-year moving average)** {.no-mobile}

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>

```{r, fig.height=4}
abm_ui_datatable_scop_snip(
  df_scop_snip,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)
```

##### **Journal impact, fractionalized (3-year moving average)** {.mobile}

```{r}
abm_ui_kable_scop_snip(df_scop_snip)
```

##### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.pdf){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis"}
cat("<hr>")
cat("This table is based on Scopus publication types Article, Review and Conference Paper.<br>")

abm_ui_note(df_scop_snip, df_coverage, unit_level, is_fractional = TRUE, is_wos = FALSE)

```
<div style='display:flex; flex-direction:row; justify-content:space-evenly; align-items:stretch;'>
<div>

##### **Field normalized journal impact (SNIP)**

```{r}
if(df_scop_snip %>% filter(!is.na(P_frac)) %>% nrow() > 0) {
  abm_graph_scop_snip(df_scop_snip)
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```  
</div>
<div>

##### **Share of publications in Top 20% journals**

```{r}
if(df_scop_snip %>% filter(!is.na(P_frac)) %>% nrow() > 0) {
  abm_graph_scop_top20(df_scop_snip)
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```  
</div>
</div>
</div>

### Co&#8209;publishing

##### **International and corporate co&#8209;publications (full counts)** {.no-mobile}

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>

```{r, fig.height = 4}
abm_ui_datatable_scop_copub(
  df_scop_copub,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)
```

##### **International and corporate co&#8209;publications (full counts)** {.mobile}

```{r}
abm_ui_kable_scop_copub(df_scop_copub)
```

##### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.pdf){target="_blank" style="position:relative;float:right;"}

```{r, echo=FALSE, results="asis"}
cat("<hr>")
cat("This table is based on Scopus publication types Article, Review and Conference Paper.<br>")

abm_ui_note(df_scop_copub, df_coverage, unit_level, is_fractional = FALSE, is_wos = FALSE)

```

<div style='display:flex; flex-direction:column; justify-content:space-evenly; align-items:center;'>

##### **International and corporate co&#8209;publication**

```{r, fig.height=4, fig.width = 8}
if(df_scop_copub %>% filter(!is.na(P_full)) %>% nrow() > 0) {
  abm_graph_scop_copub(df_scop_copub)
} else {
  shiny::HTML("<p><i>There are no publications available for this graph</i></p>")
}
```
</div>


### SDG

##### **Any Sustainable Development Goal** {.no-mobile}

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>

```{r, fig.height = 4}
abm_ui_datatable_sdg_year(
  df_sdg_year,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)
```

##### **Any Sustainable Development Goal** {.mobile}

```{r}
abm_ui_kable_sdg_year(df_sdg_year)
```

##### **Notes** [<i class="fa fa-info-circle" aria-hidden="true"></i> more...](`r STATIC`/ABM_guide.pdf){target="_blank" style="position:relative; float:right;"}

```{r, echo=FALSE, results="asis"}
cat("<hr>")
cat("This table is based on Scopus publication types Article, Review and Conference Paper.<br>")

if(isTRUE(unit_level >= 0)){

  years <- df_scop_cit %>% filter(substr(Publication_Year_ch, 1, 1) == "2") %>% pull(Publication_Year_ch) %>% as.integer()
  mincov <- df_coverage %>% filter(Publication_Type == "Peer reviewed" & Publication_Year %in% years) %>% pull(scopcov_frac) %>% min()
  minpubs <- df_coverage %>% filter(Publication_Type == "Peer reviewed" & Publication_Year %in% years) %>% pull(sumscop_full) %>% min()

  cat(glue("<span title='Legend: 75% or above is good, 60% or above is moderate while lower than 60% is poor'>Rows are based on at least <b>{minpubs}</b> (full counted) publications with ",
           "<b>{coveragetext(mincov)}</b> Scopus coverage (at least <b>{round(100*mincov, 1)}%</b>).<br>",
           "(DiVA publication types Article, peer review and Conference paper, peer review)<br></span>"))

} else {

  cat("<b>Bibliometric results for individual researchers should always be interpreted with caution.</b>")

}
cat("<hr>")
```


##### **Sustainable Development Goals** {.no-mobile}

<style type="text/css">
div.dt-buttons {
  position:relative;
  float:right;
}
</style>

```{r, fig.height = 4}
abm_ui_datatable_sdg_table(
  df_sdg_table,
  unit_file_label = unit_file_label, 
  unit_title = abm_unit_title
)
```

##### **Sustainable Development Goals** {.mobile}

```{r}
abm_ui_kable_sdg_table(df_sdg_table)
```

<i class="fa fa-info-circle" aria-hidden="true"></i> About
===========================

#### 

Row  {data-height=1024}
---------------------

<iframe allowfullscreen="true" src="https://KTH-Library.github.io/abm/About_ABM.html" style="border: 0px solid #ddd; min-height: 1024px" width="100%" height="100%" data-external="1"></iframe>

