---
title: "Introduction to usage of `bibliomatrix`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to usage of `bibliomatrix`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The main parts of the `bibliomatrix` package are:

- A public dataset for the KTH Annual Bibliometric Monitoring (ABM)
- A Shiny app and a flexdashboard layout for presenting the ABM
- Functions related to filling the ABM presentation with results

## Getting started

First load some useful packages, including `bibliomatrix`:


```{r setup, message=FALSE}
library(bibliomatrix)
library(dplyr)
library(stringr)
library(readr)
library(knitr)
library(bench)
library(DBI)
library(pool)
library(dbplyr)

if (Sys.info()["sysname"] == "Windows") 
  readRenviron(file.path(Sys.getenv("R_USER"), ".Renviron"))
```

## Data for Annual Bibliometric Monitoring (ABM)

In order to get data from the Microsoft SQL Server database, an `.Renviron` file is currently required with values being provided for the following envvars: `DBUSER` (the MSSQL Server service account name for the BIBMON db), `DBPASS`, `DBHOST` (the hostname for the MSSQL server) and `DBNAME` (use "BIBMON").

Once this has been provided in the `.Renviron` file, data for the ABM tables can be retrieved.

*NOTE: For the public part of ABM, no database connection is needed, see [Using bundled data in bibliomatrix](public-data.html).*

```{r, message=FALSE, fig.align='left'}
# Open a connection pool to Microsoft SQL Server BIBMON database
bibmon <- pool_bib("mssql")

# get data for ABM table 1
kth_data <- abm_data(bibmon, unit_code = "KTH")
t1 <- abm_table1(kth_data)

# display first few results
t1 %>% 
  slice(1:5) %>% 
  select(1:2) %>% 
  kable()

# You can build a sqlite3 databsae for local use (this will take a while the first time)
db_sync()
localdb <- pool_bib("sqlite")
kth_data_local <- abm_data(localdb, unit_code = "KTH")
t2 <- abm_table1(kth_data_local)

# are the results the same?
identical(t1, t2)

# what about performance?
bench_time(abm_table1(abm_data(con = bibmon, unit_code = "KTH")))
bench_time(abm_table1(abm_data(con = localdb, unit_code = "KTH")))

poolClose(bibmon)
poolClose(localdb)
```
